---
title: "20230505_SampleMerging_Filtering_1stPassClustering_Seurat_RNAOnly"
author: "Yusuke Koga"
date: "2023-05-05"
output:
 html_document:
     toc: true
     toc_float: true
     number_sections: true
     theme: cosmo
     code_folding: hide
---


Batch correction: Not applied

Neutrophils (Cells with low RNA library size and high CD16+ ADT): included

```{r}
suppressPackageStartupMessages({
    library(Seurat)
    library(dplyr)
    library(ggplot2)
    library(DropletUtils)
    library(singleCellTK)
    library(celda)
    library(grDevices)
    library(pheatmap)
    library(reshape2)
    library(knitr)
    library(harmony)
    library(kableExtra)
})


# Define tab levels
tab3 <- "### %s {-}
"
tab4 <- "#### %s {-}
"
tab5 <- "##### %s {-}
"
space <- "

"


```

```{r}
set.seed(12345)
```

```{r}
batchcor <- "no_harmony"
neutrophil <- "with_emptydrops"
```

# Step 1. Load all samples, merging all samples as single object

```{r, eval = FALSE}
postdeconDataDir = "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/"
allRdsObj <- list.files(path = postdeconDataDir , pattern = "*x.rds")

for(x in 1:length(allRdsObj)){
   obj <- allRdsObj[x]
   if(x > 1){
       tempObj <- readRDS(paste0(postdeconDataDir, obj))
       allSampleObj <- merge(allSampleObj, tempObj)
   }else{
       allSampleObj <- readRDS(paste0(postdeconDataDir, obj))
   }
}

# citeCounts <- GetAssayData(allSampleObj, assay = "CITE")
# citeCounts <- citeCounts[-grep("ADT",rownames(GetAssayData(allSampleObj, assay = "CITE"))),]
# allSampleObj[["CITE"]] <- CreateAssayObject(citeCounts)

saveRDS(allSampleObj, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/NeutrophilIdentification/20230220_no_combatseq_with_emptydrops_allSampleObj_PostDoubletDetection.rds")
```



# Step 2. Clustering - RNA only

Due to the CITE-seq expression data being highly variable by sample, we have decided to not integrate the CITE-seq expression (via WNN), and instead cluster the data only using RNA-seq expression.

```{r, eval = FALSE}
allSampleObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/NeutrophilIdentification/20230220_no_combatseq_with_emptydrops_allSampleObj_PostDoubletDetection.rds"))
```

```{r, eval = FALSE}
DefaultAssay(allSampleObj) = "RNA"

allSampleObj[["percent.mt"]] <-  PercentageFeatureSet(allSampleObj, pattern = "^MT-")
allSampleObj[["percent.xist"]] <-  PercentageFeatureSet(allSampleObj, pattern = "XIST")
allSampleObj[["percent.malat"]] <-  PercentageFeatureSet(allSampleObj, pattern = "MALAT")

allSampleObj[["CITE_Total"]] <- colSums(GetAssayData(allSampleObj, assay = "CITE"))
allSampleObj[["CITE_Features"]] <- colSums(GetAssayData(allSampleObj, assay = "CITE") > 0)

#Subset by demultiplex result
## Setting all samples with out HTO classifications (i.e. tumor samples that were not hashed) as singlet
allSampleObj$HTO_classification.global[which(is.na(allSampleObj$HTO_classification.global))] <- "Singlet"
```

```{r}
#QC Figure:

ggtable <- as.data.frame(as.matrix(table(allSampleObj$Batch)))

htoDemuxTable <- as.data.frame(as.matrix(table(allSampleObj$Batch,allSampleObj$HTO_classification.global == "Singlet"))[,"TRUE"])
ggtable$PostDemux <- htoDemuxTable[,1]

passDemux <- colnames(allSampleObj)[which(allSampleObj$HTO_classification.global == "Singlet")]
passCITE <- colnames(allSampleObj)[which(allSampleObj$CITE_Features > 50)]
passMT <- colnames(allSampleObj)[which(allSampleObj$percent.mt < 15)]
passDecont <- colnames(allSampleObj)[which(allSampleObj$DecontXContamination < 0.9)]

passAll <- intersect(intersect(intersect(passDemux, passCITE),passMT),passDecont)

passAllPatient <- gsub("_TL_.*","_TL", passAll)
passAllPatient <- gsub("_T_.*","_T", passAllPatient)
passAllPatient <- gsub("_L.*","_L", passAllPatient)

passQCTable <- as.data.frame(as.matrix(table(passAllPatient)))
colnames(passQCTable) <- "QC"
rownames(passQCTable) <- gsub("Patient","BUMC_LR_0",rownames(passQCTable))


#Filter to only patients 10-20
passQCTable <- passQCTable[-1,]
ggtable <- ggtable[8:25,]
ggtable <- cbind(ggtable, passQCTable)
ggtable$Sample <- c("Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor", 
                    "Patient15, LN", "Patient15, Tumor", 
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor", 
                    "Patient18, LN", "Patient18, Tumor+Normal", 
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")

colnames(ggtable)[1] <- "Non-droplets, Generated via CellRanger"
colnames(ggtable)[2] <- "Post-QC"
colnames(ggtable)[3] <- "Recovered from HTODemux, PeanutX"

ggtableM <- melt(ggtable, id.vars = "Sample")
colnames(ggtableM) <- c("Sample", "Step", "Cells")

ggtableM$Sample <- factor(ggtableM$Sample, levels = unique(ggtableM$Sample))
```


```{r, fig.width = 11, fig.height = 5}
p <- ggplot(data = ggtableM, aes(x = Sample, y = Cells, fill = Step)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))+ scale_fill_manual(values=c("red","green4", "darkblue"))
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/temp.pdf", width = 11, height = 5)
p
dev.off()
```


```{r, fig.width = 11, fig.height = 7}
adtCounts <- GetAssayData(allSampleObj, assay = "Nondecon_CITE")
adtCounts <- adtCounts[-c(1:10),]
allSampleObj[["NondeconCITE_Total"]] <- colSums(adtCounts)
metricTotalTable <- data.frame(Batch = allSampleObj$Batch, CITETotal = allSampleObj$NondeconCITE_Total)
metricTotalTable <- metricTotalTable %>% group_by(Batch) %>% summarise(average = mean(CITETotal))
metricTotalTable <- metricTotalTable[which(metricTotalTable$average > 10),]

colnames(metricTotalTable) <- c("Sample", "Average_CITE_Expression")
metricTotalTable$Sample <- c("Patient3, Tumor","Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor", 
                    "Patient15, LN", "Patient15, Tumor", 
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor", 
                    "Patient18, LN", "Patient18, Tumor+Normal", 
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")


metricTotalTable$Sample <- factor(metricTotalTable$Sample, levels = unique(metricTotalTable$Sample))

p <- ggplot(data = metricTotalTable, aes(x = Sample, y = Average_CITE_Expression, fill = Sample)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))+ ylab("Average CITE-seq Counts") + NoLegend()
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/Pardee_CITEExprs.pdf", width = 11, height = 7)
p
dev.off()
```


```{r, fig.width = 11, fig.height = 7}
adtCounts <- GetAssayData(allSampleObj, assay = "Nondecon_CITE")
adtCounts <- adtCounts[-c(1:10),]
allSampleObj[["NondeconCITE_Total"]] <- colSums(adtCounts > 0)
metricTotalTable <- data.frame(Batch = allSampleObj$Batch, CITETotal = allSampleObj$NondeconCITE_Total)
metricTotalTable <- metricTotalTable %>% group_by(Batch) %>% summarise(average = mean(CITETotal))
metricTotalTable <- metricTotalTable[which(metricTotalTable$average > 10),]

colnames(metricTotalTable) <- c("Sample", "Average_CITE_Expression")
metricTotalTable$Sample <- c("Patient3, Tumor","Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor", 
                    "Patient15, LN", "Patient15, Tumor", 
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor", 
                    "Patient18, LN", "Patient18, Tumor+Normal", 
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")


metricTotalTable$Sample <- factor(metricTotalTable$Sample, levels = unique(metricTotalTable$Sample))

p <- ggplot(data = metricTotalTable, aes(x = Sample, y = Average_CITE_Expression, fill = Sample)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))+ ylab("Average CITE-seq Features Detected") + NoLegend()
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/Pardee_CITEFeatures.pdf", width = 11, height = 7)
p
dev.off()
```


```{r, fig.width = 11, fig.height = 7}
adtCounts <- GetAssayData(allSampleObj, assay = "CITE")
allSampleObj[["CITE_Total"]] <- colSums(adtCounts > 2)
metricTotalTable <- data.frame(Batch = allSampleObj$Batch, CITETotal = allSampleObj$CITE_Total)
metricTotalTable <- metricTotalTable %>% group_by(Batch) %>% summarise(average = mean(CITETotal))
metricTotalTable <- metricTotalTable[which(metricTotalTable$average > 10),]

colnames(metricTotalTable) <- c("Sample", "Average_CITE_Expression")
metricTotalTable$Sample <- c("Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor", 
                    "Patient15, LN", "Patient15, Tumor", 
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor", 
                    "Patient18, LN", "Patient18, Tumor+Normal", 
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")


metricTotalTable$Sample <- factor(metricTotalTable$Sample, levels = unique(metricTotalTable$Sample))

p <- ggplot(data = metricTotalTable, aes(x = Sample, y = Average_CITE_Expression, fill = Sample)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))+ ylab("Average CITE-seq Features Detected, Post Decontamination") + NoLegend()
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/Pardee_CITEFeatures_PostDecon_Thres2.pdf", width = 11, height = 7)
p
dev.off()
```


```{r, fig.width = 11, fig.height = 7}
adtCounts <- GetAssayData(allSampleObj, assay = "CITE")
allSampleObj[["CITE_Total"]] <- colSums(adtCounts)
metricTotalTable <- data.frame(Batch = allSampleObj$Batch, CITETotal = allSampleObj$CITE_Total)
metricTotalTable <- metricTotalTable %>% group_by(Batch) %>% summarise(average = mean(CITETotal))
metricTotalTable <- metricTotalTable[which(metricTotalTable$average > 10),]

colnames(metricTotalTable) <- c("Sample", "Average_CITE_Expression")
metricTotalTable$Sample <- c("Patient3, Tumor","Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor", 
                    "Patient15, LN", "Patient15, Tumor", 
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor", 
                    "Patient18, LN", "Patient18, Tumor+Normal", 
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")


metricTotalTable$Sample <- factor(metricTotalTable$Sample, levels = unique(metricTotalTable$Sample))

p <- ggplot(data = metricTotalTable, aes(x = Sample, y = Average_CITE_Expression, fill = Sample)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))+ ylab("Average CITE-seq Counts, Post Decontamination") + NoLegend()
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/Pardee_CITEExprsPostDecon.pdf", width = 11, height = 7)
p
dev.off()
```

```{r, fig.width = 11, fig.height = 7}
adtCounts <- GetAssayData(allSampleObj, assay = "Nondecon_RNA")
# adtCounts <- adtCounts[-c(1:10),]
allSampleObj[["NondeconCITE_Total"]] <- colSums(adtCounts)
metricTotalTable <- data.frame(Batch = allSampleObj$Batch, CITETotal = allSampleObj$NondeconCITE_Total)
metricTotalTable <- metricTotalTable %>% group_by(Batch) %>% summarise(average = mean(CITETotal))
metricTotalTable <- metricTotalTable[which(metricTotalTable$average > 10),]

colnames(metricTotalTable) <- c("Sample", "Average_RNA_Expression")
metricTotalTable$Sample <- c("Patient3, Tumor","Patient5, Tumor+LN",
                    "Patient6, LN", "Patient6, Tumor",
                    "Patient8, LN","Patient8, Tumor", 
                    "Patient9, Tumor+LN",
                    "Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor",
                    "Patient15, LN", "Patient15, Tumor",
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor",
                    "Patient18, LN", "Patient18, Tumor+Normal",
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")


metricTotalTable$Sample <- factor(metricTotalTable$Sample, levels = unique(metricTotalTable$Sample))

p <- ggplot(data = metricTotalTable, aes(x = Sample, y = Average_RNA_Expression, fill = Sample)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))  + ylab("Average UMI Counts") + NoLegend()
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/Pardee_RNAExprs.pdf", width = 11, height = 7)
p
dev.off()
```



```{r, fig.width = 11, fig.height = 7}
adtCounts <- GetAssayData(allSampleObj, assay = "Nondecon_RNA")
# adtCounts <- adtCounts[-c(1:10),]
metricTotalTable <- data.frame(Batch = allSampleObj$Batch, CITETotal = allSampleObj$mito_percent)
metricTotalTable <- metricTotalTable %>% group_by(Batch) %>% summarise(average = mean(CITETotal))

colnames(metricTotalTable) <- c("Sample", "Average_RNA_Expression")
metricTotalTable$Sample <- c("Patient3, Tumor","Patient5, Tumor+LN",
                    "Patient6, LN", "Patient6, Tumor",
                    "Patient8, LN","Patient8, Tumor", 
                    "Patient9, Tumor+LN",
                    "Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor",
                    "Patient15, LN", "Patient15, Tumor",
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor",
                    "Patient18, LN", "Patient18, Tumor+Normal",
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")


metricTotalTable$Sample <- factor(metricTotalTable$Sample, levels = unique(metricTotalTable$Sample))

p <- ggplot(data = metricTotalTable, aes(x = Sample, y = Average_RNA_Expression, fill = Sample)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))  + ylab("Average Mitochondrial Gene Expression") + NoLegend()
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/Pardee_MitochondrialCounts.pdf", width = 11, height = 7)
p
dev.off()
```

```{r, eval = FALSE}
allSampleObj <- subset(allSampleObj, subset =  HTO_classification.global == "Singlet")

#Removing samples from patient 3
# allSampleObj <- subset(allSampleObj, subset = Patient != "Patient03")

#Also removing samples from patients 5, 6, 8, 9 as CITE-seq was not applied 
allSampleObj <- subset(allSampleObj, subset = Patient %in% c("Patient10", "Patient12", "Patient13",
                                                             "Patient14", "Patient15", "Patient16",
                                                             "Patient17", "Patient18", "Patient19", "Patient20"))

#Based on word doc (https://docs.google.com/document/d/17eF-KzMb0RcZ46tfj99cus3Gw6aXfkAk/edit), Patient 14 has several samples not applied via CITEseq, which we will remove
allSampleObj <- allSampleObj[,-intersect(which(allSampleObj$Batch == "BUMC_LR_014_T"), which(allSampleObj$HTO_classification == "ADT6"))]
allSampleObj <- allSampleObj[,-intersect(which(allSampleObj$Batch == "BUMC_LR_014_L"), which(allSampleObj$HTO_classification == "ADT9"))]
allSampleObj <- allSampleObj[,-intersect(which(allSampleObj$Batch == "BUMC_LR_014_L"), which(allSampleObj$HTO_classification == "ADT8"))]

#Empty droplets passing an ADT expression threshold were clustered, as we expected to see some "true cell" populations that had low transcript counts (i.e. neutrophils). We will take all clusters that he annotated as a likely cell population, rather than a technical artifact, which is based on the S100A8 expression (RNA) and CD16 expression (Surface protein).

allSampleObjEmpty <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/NeutrophilIdentification/no_combatseq_with_emptydrops_allSampleObj_EmptyDrops_PostSeurat_ADTClustering_WithoutHarmony.rds")

emptyBarcodesPassQC <- colnames(allSampleObjEmpty)[which(allSampleObjEmpty$ADTCluster %in% c(30, 18, 2, 6, 7, 5, 25, 26))]

emptyBarcodesPassQC <- intersect(emptyBarcodesPassQC, colnames(allSampleObj))

allSampleObjNoEmpty <- subset(allSampleObj, EmptyDroplet != "EmptyDroplet")
allSampleObjEmpty <- allSampleObjEmpty[,emptyBarcodesPassQC]

allSampleObjEmptySub <- allSampleObj[,emptyBarcodesPassQC]
allSampleObjEmptySub$EmptyADTCluster <- allSampleObjEmpty$ADTCluster

rm(allSampleObjEmpty)

allSampleObj <- merge(allSampleObjNoEmpty, allSampleObjEmptySub)

rm(allSampleObjEmptySub)
rm(allSampleObjNoEmpty)
gc()

saveRDS(allSampleObj, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/1stPass/20230505_Removed_NonNeutrophilEmptyDroplets_Patients3_5_6_8_9_HTODoublets.rds") #88874 cells passing above thresholds

#Remove all cells that display high ADT contamination level
allSampleObj <- allSampleObj[,-which(allSampleObj$DecontXContamination > 0.9)]

#Subset by number of CITE-seq features detected
allSampleObj <- subset(allSampleObj, subset =  CITE_Features > 50)
#Subset by mitochondrial gene expression percentage
allSampleObj <- subset(allSampleObj, subset =  percent.mt < 15)

# dim(allSampleObj) #84739 cells passing above thresholds (84739/88874, less than 15% mito, > 50 CITE, < 0.9 DecontX)
```

```{r, eval = FALSE}
allSampleObj = NormalizeData(allSampleObj, verbose = FALSE) %>%
  FindVariableFeatures(selection.method = 'vst', verbose = FALSE) %>%
  ScaleData(verbose = FALSE) %>%
  RunPCA(verbose = FALSE) 

# ElbowPlot(allSampleObj, ndims = 40)

allSampleObj<- FindNeighbors(allSampleObj, dims = 1:30, verbose = FALSE, reduction = "pca")
allSampleObj <- FindClusters(allSampleObj, resolution = 1.0, verbose = FALSE)
allSampleObj <- RunUMAP(allSampleObj, reduction = "pca", dims=1:30, verbose = FALSE)

allSampleObj[["RNACluster"]] <- Idents(allSampleObj)


#Add hashtag infos
sampleInfoTable <- data.frame(Patient = allSampleObj$Patient,
                              TumorOnly = allSampleObj$OnlyTumor,
                              Hashtag = allSampleObj$HTO_classification)

lymphInfo <- sapply(1:nrow(sampleInfoTable),function(z){
    y = sampleInfoTable[z,"Patient"]
    x = sampleInfoTable[z,"Hashtag"]
    if(is.na(x)){
        return("Tumor")
    }else{
        if(y == "Patient10"){
            if(x == "ADT8"){
                return("Tumor")
            }else{
                return("Lymph_4R")
            }
        }else if(y == "Patient06"){
            if(x == "ADT6"){
                return("Lymph_9")
            }else if(x == "ADT7"){
                return("Lymph_4R")
            }else if(x == "ADT8"){
                return("Lymph_7")
            }else if(x == "ADT9"){
                return("Lymph_12R")
            }
        }else if(y == "Patient08"){
            if(x == "ADT6"){
                return("Lymph_9")
            }else if(x == "ADT7"){
                return("Lymph_10L")
            }else if(x == "ADT8"){
                return("Lymph_7")
            }else if(x == "ADT9"){
                return("Lymph_5")
            }
        }else if(y == "Patient09"){
            if(x == "ADT6"){
                return("Tumor")
            }else if(x == "ADT7"){
                return("Lymph_7")
            }else if(x == "ADT8"){
                return("Lymph_9")
            }
        }else if(y == "Patient12"){
            if(x == "ADT5"){
                return("Lymph_9")
            }else if(x == "ADT6"){
                return("Lymph_7")
            }else if(x == "ADT7"){
                return("Lymph_4R")
            }else if(x == "ADT8"){
                return("Lymph_10R")
            }else if(x == "ADT9"){
                return("Lymph_12R")
            }else if(x == "ADT10"){
                return("Tumor")
            }
        }else if(y == "Patient14"){
            if(x == "ADT5"){
                return("Lymph_5")
            }else if(x == "ADT6"){
                return("Lymph_8")
            }else if(x == "ADT7"){
                return("Lymph_7")
            }else if(x == "ADT8"){
                return("Lymph_10L")
            }else if(x == "ADT9"){
                return("Lymph_9")
            }else if(x == "ADT10"){
                return("Lymph_10L")
            }
        }else if(y == "Patient15"){
            if(x == "ADT7"){
                return("Lymph_5")
            }else if(x == "ADT8"){
                return("Lymph_10L")
            }else if(x == "ADT9"){
                return("Lymph_9")
            }
        }else if(y == "Patient16"){
            if(x == "ADT5"){
                return("Lymph_7")
            }else if(x == "ADT6"){
                return("Lymph_11R")
            }else if(x == "ADT7"){
                return("Lymph_4R")
            }else if(x == "ADT8"){
                return("Lymph_10R")
            }
        }else if(y == "Patient17"){
            if(x == "ADT5"){
                return("Lymph_9")
            }else if(x == "ADT6"){
                return("Lymph_7")
            }else if(x == "ADT7"){
                return("Lymph_4R")
            }
        }else if(y == "Patient18"){
            if(x == "ADT5"){
                return("Lymph_7")
            }else if(x == "ADT6"){
                return("Lymph_7")
            }else if(x == "ADT7"){
                return("Lymph_10L")
            }else if(x == "ADT8"){
                return("Lymph_5")
            }else if(x == "ADT9"){
                return("Tumor")
            }else if(x == "ADT10"){
                return("Normal")
            }
        }else if(y == "Patient19"){
            if(x == "ADT5"){
                return("Lymph_7")
            }else if(x == "ADT6"){
                return("Lymph_4R")
            }else if(x == "ADT7"){
                return("Lymph_11R")
            }else if(x == "ADT8"){
                return("Lymph_10R")
            }else if(x == "ADT9"){
                return("Tumor")
            }else if(x == "ADT10"){
                return("Normal")
            }
        }else if(y == "Patient20"){
            if(x == "ADT5"){
                return("Lymph_8")
            }else if(x == "ADT6"){
                return("Lymph_7")
            }else if(x == "ADT7"){
                return("Lymph_10L")
            }else if(x == "ADT8"){
                return("Lymph_5")
            }else if(x == "ADT9"){
                return("Tumor")
            }else if(x == "ADT10"){
                return("Normal")
            }
        }
    }
})

allSampleObj$HashedInfo <- lymphInfo
allSampleObj$SampleInfo <- paste(allSampleObj$Patient, allSampleObj$HashedInfo, sep = "_")


#Getting consensus doublet info
doubletDf <- data.frame(scDblFinder = allSampleObj$scDblFinder_doublet_call,
                        cxds = allSampleObj$scds_cxds_call,
                        bcds = allSampleObj$scds_bcds_call,
                        hybrid = allSampleObj$scds_hybrid_call)

consensusDoublet <- apply(doubletDf, 1, function(x){
    return(sum(x == "Doublet"))
})

consensusDoublet <- ifelse(consensusDoublet > 2, "Doublet", "Singlet")

allSampleObj$ConsensusDoublet <- consensusDoublet

#Editing error found:
allSampleObj$Lymph_Tumor_Normal <- gsub("_.*","",allSampleObj$HashedInfo)
allSampleObj$SampleInfo[which(allSampleObj$Batch == "BUMC_LR_014_T")] <- "Patient14_Tumor"
allSampleObj$Lymph_Tumor_Normal[which(allSampleObj$Batch == "BUMC_LR_014_T")] <- "Tumor"

saveRDS(allSampleObj, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/1stPass/20230505_no_harmony_allSampleObj_PostSeurat_RNAOnlyClustering_DecontXThres.rds")
```

```{r}
allSampleObj <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/1stPass/20230505_no_harmony_allSampleObj_PostSeurat_RNAOnlyClustering_DecontXThres.rds")
```


## UMAP {.tabset}

### Seurat Cluster

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, label = TRUE)
```

### Batch

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, group.by = "Batch")
```

### Patient

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, group.by = "Patient")
```

### Patient + Sample origin

```{r, fig.width = 14, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, group.by = "SampleInfo")
```

### Doublet call, consensus

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, group.by = "ConsensusDoublet")
```

### Lymph/Tumor/Normal

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
allSampleObj$Lymph_Tumor_Normal <- gsub("_.*","",allSampleObj$HashedInfo)
DimPlot(allSampleObj, group.by = "Lymph_Tumor_Normal")
```

### Empty droplet

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, group.by = "EmptyDroplet")
```

### RNA markers {.tabset}

#### CD3D

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "CD3D", reduction = "umap")
```

#### CD4

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "CD4", reduction = "umap")
```

#### IL7R

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "IL7R", reduction = "umap")
```

#### CD8A

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "CD8A", reduction = "umap")
```

#### NKG7

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "NKG7", reduction = "umap")
```

#### CD56

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "NCAM1", reduction = "umap")
```

#### CD14

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "CD14", reduction = "umap")
```

#### CD16

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "FCGR3A", reduction = "umap")
```

#### MARCO

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "MARCO", reduction = "umap")
```


#### CD1C

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "CD1C", reduction = "umap")
```

#### MS4A1

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "MS4A1", reduction = "umap")
```

#### MZB1

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "MZB1", reduction = "umap")
```

#### CD19

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "CD19", reduction = "umap")
```

#### TPSAB1

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "TPSAB1", reduction = "umap")
```

#### IRF7

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "IRF7", reduction = "umap")
```

#### IL3RA

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "IL3RA", reduction = "umap")
```

#### S100A8

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "S100A8", reduction = "umap")
```

#### EPCAM

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "EPCAM", reduction = "umap")
```


## Broad clustering of cell types

```{r}
allSampleObj$BroadClustering1Pass <-
    sapply(allSampleObj$RNACluster, function(x){
    if(x %in% c(30)){
        return("Mast")
    }else if(x %in% c(19, 20, 22, 32)){
        return("Epithelial")
    }else if(x %in% c(27)){
        return("pDC")
    }else if(x %in% c(18, 23)){
        return("Plasma")
    }else if(x %in% c(3, 14, 29)){
        return("B")
    }else if(x %in% c(0, 1, 2, 5,
                      7, 9, 10, 12, 13,
                      14, 17, 25)){
        return("TNK")
    }else if(x %in% c(6,31)){
        return("Neutrophil")
    }else{
        return("Myeloid")
    }
})


#B - 8109 cells
#Epithelial - 3471 cells
#Mast - 347 cells
#Myeloid - 18086 cells
#Neutrophil - 4455 cells
#Plasma - 2089 cells
#TNK - 47629 cells
#pDC - 553 cells
```

```{r}
allSampleObj$BroadClustering1Pass <- factor(allSampleObj$BroadClustering1Pass,
                                               levels = rev(rev(c("TNK", "B", "Plasma", "pDC","Myeloid",
                                                           "Neutrophil",
                                                          "Mast", "Epithelial"))))
DimPlot(allSampleObj, group.by = "BroadClustering1Pass", label = TRUE)
pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/AllCellTypesCombined/Celltype_p1.pdf",
width = 9, height = 6)
DimPlot(allSampleObj, group.by = "BroadClustering1Pass", label = FALSE) + NoLegend()
dev.off()

pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/AllCellTypesCombined/Celltype_p1_tnl.pdf", width = 9, height = 6)
DimPlot(allSampleObj, group.by = "Lymph_Tumor_Normal", label = FALSE, cols = c("blue","green3","red")) + NoLegend()
dev.off()


```


```{r, eval = FALSE}
# #Saving subsetted Seurat object

tnkObj <- subset(allSampleObj, BroadClustering1Pass %in% c("TNK"))
bCellObj <- subset(allSampleObj, BroadClustering1Pass %in% c("B"))
plasmaObj <- subset(allSampleObj, BroadClustering1Pass %in% c("Plasma"))
myeloidObj <- subset(allSampleObj, BroadClustering1Pass %in% c("Myeloid", "cDCs", "Alveolar Macs"))
neutrophilObj <- subset(allSampleObj, BroadClustering1Pass %in% "Neutrophil")
epithelialObj <- subset(allSampleObj, BroadClustering1Pass %in% "Epithelial")
mastObj <- subset(allSampleObj, BroadClustering1Pass %in% "Mast")
pdcObj <- subset(allSampleObj, BroadClustering1Pass %in% "pDC")

saveRDS(tnkObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/TNK/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_TNK.rds"))
saveRDS(bCellObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/BCell/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_BCell.rds"))
saveRDS(plasmaObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/Plasma/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_Plasma.rds"))
saveRDS(myeloidObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/Myeloid/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_Myeloid.rds"))
saveRDS(neutrophilObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/Neutrophil/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_Neutrophil.rds"))
saveRDS(epithelialObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/Epithelial/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_Epithelial.rds"))
saveRDS(mastObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/Mast/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_Mast.rds"))
saveRDS(pdcObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/pDC/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_pDC.rds"))

```

## Violin Plots {.tabset}

### CD3D

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "CD3D")
```

### CD56

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "NCAM1")
```

### CD14

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "CD14")
```

### CD16

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "FCGR3A")
```

### CD1C

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "CD1C")
```

### LAMP3

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "LAMP3")
```

### MS4A1

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "MS4A1")
```

### CD19

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "CD19")
```

### MZB1

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "MZB1")
```

### IL3RA

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "IL3RA")
```

### EPCAM

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "EPCAM")
```


### S100A8

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "S100A8")
```


### TPSAB1

```{r, fig.width = 10, fig.height= 4}
VlnPlot(allSampleObj, "TPSAB1")
```


```{r, eval = FALSE}
bCellObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/BCell/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_BCell.rds"))
bCellObjLymph <- subset(bCellObj, subset = Lymph_Tumor_Normal == "Lymph")

bCellBarcodes <- colnames(bCellObjLymph)

tail(bCellBarcodes)
bCellBarcodes <- gsub("-1", "", bCellBarcodes)
bCellBarcodes <- grep("Patient20", bCellBarcodes, value = TRUE)
bCellBarcodes <- gsub("Patient20_L_", "", bCellBarcodes)

whiteList <- read.table("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Fastq/2021-12-03/outs/fastq_path/AAAJGCJHV/whitelist2.txt", sep = "\t")


intersectingBarcodesFromWL <- intersect(bCellBarcodes, whiteList$V1)

whiteListSub <- whiteList[which(whiteList$V1 %in% intersectingBarcodesFromWL),]

write.table(whiteListSub, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Fastq/2021-12-03/outs/fastq_path/AAAJGCJHV/whitelist_bcell.txt", sep = "\t", quote = FALSE, row.names = FALSE, col.names = FALSE)
```



```{r}
allSampleObj$Lymph_Tumor_Normal
table(allSampleObj$BroadClustering1Pass, allSampleObj$Patient)
```

```{r, fig.width = 4, fig.height = 3}
allSampleObjLymph <- subset(allSampleObj, subset = Lymph_Tumor_Normal == "Lymph")
ggTable <- table(allSampleObjLymph$BroadClustering1Pass, allSampleObjLymph$Patient) %>% prop.table(2) %>% melt()

pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230410_AACR/20230425_barbypatientln.pdf", width = 4.25, height = 2.75)
colnames(ggTable) <- c("CellType", "Patient", "Proportion")
ggplot(ggTable, aes(x = Patient, y = Proportion, fill = CellType)) + geom_bar(stat = "identity") + theme_classic()  + scale_y_continuous(expand = c(0, 0)) + theme(axis.text.x = element_text(angle = 45, hjust=1))
dev.off()

allSampleObjTumor <- subset(allSampleObj, subset = Lymph_Tumor_Normal == "Tumor")
ggTable <- table(allSampleObjTumor$BroadClustering1Pass, allSampleObjTumor$Patient) %>% prop.table(2) %>% melt()

pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230410_AACR/20230425_barbypatienttumor.pdf", width = 4.5, height = 2.75)
colnames(ggTable) <- c("CellType", "Patient", "Proportion")
ggplot(ggTable, aes(x = Patient, y = Proportion, fill = CellType)) + geom_bar(stat = "identity") + theme_classic()  + scale_y_continuous(expand = c(0, 0)) + theme(axis.text.x = element_text(angle = 45, hjust=1))
dev.off()


allSampleObjNormal <- subset(allSampleObj, subset = Lymph_Tumor_Normal == "Normal")
ggTable <- table(allSampleObjNormal$BroadClustering1Pass, allSampleObjNormal$Patient) %>% prop.table(2) %>% melt()

pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230410_AACR/20230425_barbypatientnormal.pdf", width = 2.75, height = 2.75)
colnames(ggTable) <- c("CellType", "Patient", "Proportion")
ggplot(ggTable, aes(x = Patient, y = Proportion, fill = CellType)) + geom_bar(stat = "identity") + theme_classic()  + scale_y_continuous(expand = c(0, 0)) + theme(axis.text.x = element_text(angle = 45, hjust=1))
dev.off()
```



```{r}
fm <- FindAllMarkers(allSampleObj)
saveRDS(fm, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/",sampleType,"/20230505_Seurat_3rdPass_Multimodal_FindMarkers_RNA_",sampleType,".rds"))

DefaultAssay(allSampleObj) <- "CITE"
allMarkersADT <- FindAllMarkers(allSampleObj,test.use = "MAST", latent.vars = "Batch", verbose = FALSE)
saveRDS(allMarkersADT, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/",sampleType,"/20230505_Seurat_3rdPass_Multimodal_FindMarkers_ADT_",sampleType,".rds"))
```

# Scatter plot for CITE-seq expression, total

```{r, fig.width = 10, fig.height = 5}
allSampleObj$nCount_CITE <- colSums(GetAssayData(allSampleObj, assay = "CITE"))
allSampleObj$PatientSample <- paste0(allSampleObj$Patient, allSampleObj$Lymph_Tumor_Normal)
VlnPlot(allSampleObj, "nCount_CITE", group.by = "PatientSample", pt.size = 0.25) + NoLegend() + ggtitle("Total CITE-seq expression per cell")
```

```{r}
library(Seurat)
```

```{r, eval = FALSE}
#4/26/23 - Create Fastq file for B cells taken from LN of Patient 20 

bCellObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/BCell/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_BCell.rds"))
bCellObjLymph <- subset(bCellObj, subset = Lymph_Tumor_Normal == "Lymph")

bCellBarcodes <- colnames(bCellObjLymph)

tail(bCellBarcodes)
bCellBarcodes <- gsub("-1", "", bCellBarcodes)
bCellBarcodes <- grep("Patient20", bCellBarcodes, value = TRUE)
bCellBarcodes <- gsub("Patient20_L_", "", bCellBarcodes)

whiteList <- read.table("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Fastq/2021-12-03/outs/fastq_path/AAAJGCJHV/whitelist2.txt", sep = "\t")


intersectingBarcodesFromWL <- intersect(bCellBarcodes, whiteList$V1)

whiteListSub <- whiteList[which(whiteList$V1 %in% intersectingBarcodesFromWL),]

write.table(whiteListSub, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Fastq/2021-12-03/outs/fastq_path/AAAJGCJHV/whitelist_bcell.txt", sep = "\t", quote = FALSE, row.names = FALSE, col.names = FALSE)
```

```{r, eval = FALSE}
# 4/27/23 - Send barcodes for B cells

barcodeDF <- data.frame(Barcode = colnames(bCellObj))
barcodeDF$Patient <- gsub("_.*", "", barcodeDF$Barcode)

barcodeDF$SampleID <- gsub("_.{16}-1", "", barcodeDF$Barcode)
barcodeDF$SampleID <- gsub("Patient", "LR_0", barcodeDF$SampleID)
barcodeDF$Barcode <- gsub(".*_","",barcodeDF$Barcode)
barcodeDF$Barcode <- gsub("-1","",barcodeDF$Barcode)

dirDF <- data.frame(Filepath = list.files(path = "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Fastq", pattern = "_S[13579]_L001_R1_001.fastq.gz", recursive = TRUE, include.dirs = TRUE, full.names = TRUE))

dirDF$Sample <- gsub("_L001_R1_001.fastq.gz","",dirDF$Filepath)
dirDF$Sample <- gsub("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Fastq/.*/","",dirDF$Sample) 
dirDF$Sample <- gsub(".*LR","LR",dirDF$Sample) 
dirDF$Sample <- gsub("_A.*","",dirDF$Sample) 
dirDF$Sample <- gsub("_B.*","",dirDF$Sample) 

dirDF <- dirDF[which(dirDF$Sample %in% intersect(dirDF$Sample, barcodeDF$SampleID)),]

dirDF$Filepath <- gsub("/CJ.*fastq.gz","/",dirDF$Filepath)
dirDF$Filepath <- gsub("/XC.*fastq.gz","/",dirDF$Filepath)

finalDF <- merge(barcodeDF, dirDF, by.x = "SampleID", by.y = "Sample")

write.csv(finalDF, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/1stPass/20230427_ShareWithDarren_BLymphocytes.csv")
```

```{r}
dfTable <- table(allSampleObj$BroadClustering1Pass, allSampleObj$Batch) %>% prop.table(2)
allSampleObj$nCount_CITE <- colSums(GetAssayData(allSampleObj, assay = "CITE"))
citeTable <- data.frame(CITE = allSampleObj$nCount_CITE, 
                        Sample = allSampleObj$Batch)

citeTable  %>% group_by(Sample) %>% 
  summarise(mean_citeExprs=mean(CITE),
            .groups = 'drop') -> citeTableGrouped
```


```{r, fig.width=14, fig.height=7}
plot(citeTableGrouped$mean_citeExprs, dfTable["Neutrophil",], pch = 20)
text(citeTableGrouped$mean_citeExprs, dfTable["Neutrophil",],labels = (citeTableGrouped$Sample))
```




```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "CD3D", reduction = "umap", max.cutoff = 15, cols = c("gray90", "blue"))
```



```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "RNA"
FeaturePlot(allSampleObj, "IRF7", reduction = "umap", max.cutoff = 15, cols = c("gray90", "blue"))
```

```{r, eval = TRUE}
DefaultAssay(allSampleObj) <- "CITE"
FeaturePlot(allSampleObj, "CD45RA", reduction = "umap", max.cutoff = 25, cols = c("gray90", "darkgreen"))
```
