---
title: "Step 1. Preprocessing and quality control of CITE-seq data"
author: "Yusuke Koga"
date: "2025-03-20"
output: html_document
---

```{r}
suppressPackageStartupMessages({
    library(imcRtools)
    library(dittoSeq)
    library(cytomapper)
    library(tidyverse)
    library(viridis)
    library(RColorBrewer)
    library(Rphenograph)
    library(gridExtra)
    library(viridis)
    library(BiocSingular)
    library(cowplot)
    library(scater)
    library(patchwork)
    library(Seurat)
    library(scales)
    library(celda)
    library(singleCellTK)
    library(sva)
    library(pheatmap)
    library(ggrepel)
    library(scran)
    library(reshape)
    library(data.table)
    library(monocle3)
    library(sccomp)
    library(knitr)
    library(kableExtra)
    library(DescTools)
})

set.seed(12345)

# Define tab levels
tab2 <- "## %s {-}
"
tab3 <- "### %s {-}
"
tab4 <- "#### %s {-}
"
tab5 <- "##### %s {-}
"

space <- "

"
```

# Step 1-1. Run CellRanger to align sequencing reads and generating expression counts

* This is done using a bash script for multithreading (/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Alignment/Scripts/XiC_2022-1123_CellRanger.sh)

* The output was deposited in /restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Alignment/20221122_NewAlignment.

# Step 1-2. Run a pipeline script for QC and decontamination
* Steps 1-2 was run using a pipeline script that was submitted as a batch job: /restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/Scripts/20230211_Demux_Decon_QC/20230211_decon_demux.sh, which calls /restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/Scripts/20230131_PeanutX_DecontX_HTODemux_QC.R

```{r}
##### Below code was run per multiplexed sample #####
# For purposes of this code, we will set filename as ""
filename <- "BUMC_LR_019_L"
datadir <- "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Data/Alignment/20221122_NewAlignment/"
outputdir <- "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/20230211_Post_Demux_Decon_QC/"

## Step 1-2-1: Read in CellRanger output

## List of sample and corresponding HTO used for hashtagging
htoList = list("BUMC_LR_003_L"= c("ADT6-TotalSeqC", "ADT7-TotalSeqC",
                                  "ADT8-TotalSeqC", "ADT9-TotalSeqC"),
               "BUMC_LR_003_T"= c("Tumor"),
               "BUMC_LR_005_TL"= c("ADT6-TotalSeqC", "ADT7-TotalSeqC",
                                   "ADT8-TotalSeqC", "ADT9-TotalSeqC"),
               "BUMC_LR_006_T"= c("Tumor"),
               "BUMC_LR_006_L"= c("ADT6-TotalSeqC", "ADT7-TotalSeqC",
                                  "ADT8-TotalSeqC", "ADT9-TotalSeqC"),
               "BUMC_LR_008_TA"= c("Tumor"),
               "BUMC_LR_008_L"= c("ADT6-TotalSeqC", "ADT7-TotalSeqC",
                                   "ADT8-TotalSeqC", "ADT9-TotalSeqC"),
               "BUMC_LR_009_TL"= c("ADT6-TotalSeqC", "ADT7-TotalSeqC", "ADT8-TotalSeqC"),
               "BUMC_LR_010_TL"= c("ADT8-TotalSeqC", "ADT9-TotalSeqC"),
               "BUMC_LR_013_T"= c("Tumor"),
               "BUMC_LR_012_L"= c("ADT5-TotalSeqC", "ADT6-TotalSeqC",
                                  "ADT7-TotalSeqC", "ADT8-TotalSeqC"),
               "BUMC_LR_012_TL"= c("ADT9-TotalSeqC","ADT10-TotalSeqC"),
               "BUMC_LR_014_L" = c("ADT5-TotalSeqC", "ADT6-TotalSeqC",
                                   "ADT7-TotalSeqC", "ADT8-TotalSeqC",
                                   "ADT9-TotalSeqC", "ADT10-TotalSeqC"),
               "BUMC_LR_014_T" = c("Tumor"),
               "BUMC_LR_015_L"= c("ADT7-TotalSeqC","ADT8-TotalSeqC", "ADT9-TotalSeqC"),
               "BUMC_LR_015_T"= c("Tumor"),
               "BUMC_LR_016_L"= c("ADT5-TotalSeqC", "ADT6-TotalSeqC",
                                  "ADT7-TotalSeqC", "ADT8-TotalSeqC"),
               "BUMC_LR_016_T"= c("Tumor"),
               "BUMC_LR_017_L"= c("ADT5-TotalSeqC", "ADT6-TotalSeqC",
                                  "ADT7-TotalSeqC"),
               "BUMC_LR_017_T"= c("Tumor"),
               "BUMC_LR_018_L"= c("ADT5-TotalSeqC", "ADT6-TotalSeqC",
                                  "ADT7-TotalSeqC", "ADT8-TotalSeqC"),
               "BUMC_LR_018_T"= c("ADT9-TotalSeqC", "ADT10-TotalSeqC"),
               "BUMC_LR_019_L"= c("ADT5-TotalSeqC", "ADT6-TotalSeqC",
                                  "ADT7-TotalSeqC", "ADT8-TotalSeqC"),
               "BUMC_LR_019_T"= c("ADT9-TotalSeqC", "ADT10-TotalSeqC"),
               "BUMC_LR_020_L"= c("ADT5-TotalSeqC", "ADT6-TotalSeqC",
                                  "ADT7-TotalSeqC", "ADT8-TotalSeqC"),
               "BUMC_LR_020_T"= c("ADT9-TotalSeqC", "ADT10-TotalSeqC"))


#Samples where CITEseq/TotalSeq not applied
noCITEseq = c("BUMC_LR_005_TL", "BUMC_LR_006_T", "BUMC_LR_006_L", "BUMC_LR_008_TA",
              "BUMC_LR_008_T", "BUMC_LR_008_L", "BUMC_LR_009_TL")

htos = htoList[[filename]]

htos = gsub("-TotalSeqC", "", htos)
batch = paste0("Patient", gsub("BUMC_LR_0","",filename))
patient = gsub("_.*","",batch)
# read raw data using the Seurat function "Read10X"

filtData <- Read10X(paste0(datadir, filename, "/outs/filtered_feature_bc_matrix/"))
gex_filtered <- SingleCellExperiment(list(counts = filtData[["Gene Expression"]]))
adt_filtered <- SingleCellExperiment(list(counts = filtData[["Antibody Capture"]]))

rawData <- Read10X(paste0(datadir, filename, "/outs/raw_feature_bc_matrix/"))
gex_raw <- SingleCellExperiment(list(counts = rawData[["Gene Expression"]]))
adt_raw <- SingleCellExperiment(list(counts = rawData[["Antibody Capture"]]))

gex_filtered$EmptyDroplet <- "Cell"
adt_filtered$EmptyDroplet <- "Cell"


## Step 1-2-2: Identify low-transcript populations that are likely to be neutrophils
if(!(filename %in% noCITEseq)){
    #Compare total RNA and ADT library size
    cellIx <- ifelse(colnames(adt_raw) %in% colnames(adt_filtered), "Cell", "Droplet")

    dfExprs = data.frame(RNAExp = log2(colSums(counts(gex_raw)) + 1),
                         ADTExp = log2(colSums(counts(adt_raw)) + 1),
                         Cell = cellIx,
                         CD16ADT = log2(counts(adt_raw)["CD16_TotalSeqC",] + 1))


    p1 <- ggplot(dfExprs, aes(x = RNAExp, y = ADTExp, color = Cell)) + geom_point() +
        theme_classic() + ggtitle("Empty Droplet Call, 10X")

    png(paste0(outputdir,"/",filename,"_RNA_ADT_Library.png"))
    print(p1)
    dev.off()

    neutrophilThres <- max(log2(counts(adt_raw)["CD16_TotalSeqC",] + 1)) / 2
    adtTotalThres <- sd(log2(colSums(counts(adt_raw)) + 1)) * 2 +  mean(log2(colSums(counts(adt_raw)) + 1))
    # sd(log2(counts(adt_raw)["CD16_TotalSeqC",] + 1)) * 4 +  mean(log2(counts(adt_raw)["CD16_TotalSeqC",] + 1))
    # sd(log2(colSums(counts(adt_raw)) + 1)) * 2 +  mean(log2(colSums(counts(adt_raw)) + 1))

    p2 <- ggplot(dfExprs, aes(x = RNAExp, y = ADTExp, color = CD16ADT)) + geom_point() +
        scale_colour_gradient2(low = "black", mid = "darkblue", high = "green") +
        theme_classic() + ggtitle("CD16 ADT Expression") +
        geom_hline(yintercept=adtTotalThres, linetype="dashed", color = "red")

    png(paste0(outputdir,"/",filename,"_ADT_CD16_Library.png"))
    print(p2)
    dev.off()

    neutrophil.ix <- intersect(intersect(intersect(which(log2(counts(adt_raw)["CD16_TotalSeqC",] + 1) > neutrophilThres),
                               which(log2(colSums(counts(adt_raw)) + 1) > adtTotalThres)),
                               which(log2(colSums(counts(gex_raw)) + 1) > 5)),
                               which(cellIx == "Droplet"))
    gex_neutrophil <- gex_raw[,neutrophil.ix]
    adt_neutrophil <- adt_raw[,neutrophil.ix]
    gex_neutrophil$EmptyDroplet <- "EmptyDroplet"
    adt_neutrophil$EmptyDroplet <- "EmptyDroplet"

    gex_filtered <- cbind(gex_filtered, gex_neutrophil)
    adt_filtered <- cbind(adt_filtered, adt_neutrophil)
}


if(!(filename %in% noCITEseq)){
    #Compare total RNA and ADT library size
    cellIx <- ifelse(colnames(adt_raw) %in% colnames(adt_filtered), "Cell", "Droplet")

    dfExprs = data.frame(RNAExp = log2(colSums(counts(gex_raw)) + 1),
                         ADTExp = log2(colSums(counts(adt_raw)) + 1),
                         Cell = cellIx,
                         CD16ADT = log2(counts(adt_raw)["CD16_TotalSeqC",] + 1))


    p1 <- ggplot(dfExprs, aes(x = RNAExp, y = ADTExp, color = Cell)) + geom_point() +
        theme_classic() + ggtitle("Empty Droplet Call, 10X")
    print(p1)

    neutrophilThres <- max(log2(counts(adt_raw)["CD16_TotalSeqC",] + 1)) / 2
    adtTotalThres <- sd(log2(colSums(counts(adt_raw)) + 1)) * 2 +  mean(log2(colSums(counts(adt_raw)) + 1))

    p2 <- ggplot(dfExprs, aes(x = RNAExp, y = ADTExp, color = CD16ADT)) + geom_point() +
        scale_colour_gradient2(low = "black", mid = "darkblue", high = "green") +
        theme_classic() + ggtitle("CD16 ADT Expression") +
        geom_hline(yintercept=adtTotalThres, linetype="dashed", color = "red")
    print(p2)


    neutrophil.ix <- intersect(intersect(intersect(which(log2(counts(adt_raw)["CD16_TotalSeqC",] + 1) > neutrophilThres),
                               which(log2(colSums(counts(adt_raw)) + 1) > adtTotalThres)),
                               which(log2(colSums(counts(gex_raw)) + 1) > 5)),
                               which(cellIx == "Droplet"))
    gex_neutrophil <- gex_raw[,neutrophil.ix]
    adt_neutrophil <- adt_raw[,neutrophil.ix]
    gex_neutrophil$EmptyDroplet <- "EmptyDroplet"
    adt_neutrophil$EmptyDroplet <- "EmptyDroplet"

    gex_filtered <- cbind(gex_filtered, gex_neutrophil)
    adt_filtered <- cbind(adt_filtered, adt_neutrophil)
}
    

## Step 1-2-3: Apply decontX for decontamination of RNA expression
cell.rna.raw <- as.matrix(counts(gex_filtered))

## Check to see if all barcodes have expression data
if(!all((colSums(cell.rna.raw) > 0))){
    adt_filtered <- adt_filtered[,which(colSums(cell.rna.raw) > 0)]
    gex_filtered <- gex_filtered[,which(colSums(cell.rna.raw) > 0)]
    cell.rna.raw <- as.matrix(counts(gex_filtered))
}

cell.rna.decont = celda::decontX(cell.rna.raw, background = counts(gex_raw), verbose = FALSE)

## Add batch info to cell barcode
colnames(cell.rna.raw) <- paste0(batch,"_",colnames(cell.rna.raw))
colnames(cell.rna.decont$decontXcounts) <- paste0(batch,"_",colnames(cell.rna.decont$decontXcounts))

## Create Seurat object, note: min.cells is a gene filter, not a cell filter
seuratObj = Seurat::CreateSeuratObject(counts = cell.rna.decont$decontXcounts,
                                       assay = "RNA",
                                       min.cells = 20)

seuratObj[["Nondecon_RNA"]] = Seurat::CreateAssayObject(data = cell.rna.raw)

## Remove the "_TotalSeqC" suffix
rownames(adt_filtered) = gsub("_TotalSeqC","",rownames(adt_filtered))
cell.adt.filtered.nodecon <- as.matrix(counts(adt_filtered))
colnames(cell.adt.filtered.nodecon) <- paste0(batch,"_",colnames(cell.adt.filtered.nodecon))
seuratObj[["Nondecon_CITE"]] = Seurat::CreateAssayObject(data = cell.adt.filtered.nodecon)
```


# Step 2-1. 1st-pass clustering

```{r}
batchcor <- "no_harmony"
neutrophil <- "with_emptydrops"
```



```{r, eval = FALSE}
# Step 1. Load all samples, merging all samples as single object
postdeconDataDir = "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/"
allRdsObj <- list.files(path = postdeconDataDir , pattern = "*x.rds")

for(x in 1:length(allRdsObj)){
   obj <- allRdsObj[x]
   if(x > 1){
       tempObj <- readRDS(paste0(postdeconDataDir, obj))
       allSampleObj <- merge(allSampleObj, tempObj)
   }else{
       allSampleObj <- readRDS(paste0(postdeconDataDir, obj))
   }
}

# citeCounts <- GetAssayData(allSampleObj, assay = "CITE")
# citeCounts <- citeCounts[-grep("ADT",rownames(GetAssayData(allSampleObj, assay = "CITE"))),]
# allSampleObj[["CITE"]] <- CreateAssayObject(citeCounts)

# saveRDS(allSampleObj, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/NeutrophilIdentification/20230220_no_combatseq_with_emptydrops_allSampleObj_PostDoubletDetection.rds")
```


```{r, eval = FALSE}
allSampleObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/NeutrophilIdentification/20230220_no_combatseq_with_emptydrops_allSampleObj_PostDoubletDetection.rds"))
```

```{r, eval = FALSE}
DefaultAssay(allSampleObj) = "RNA"

allSampleObj[["percent.mt"]] <-  PercentageFeatureSet(allSampleObj, pattern = "^MT-")
allSampleObj[["percent.xist"]] <-  PercentageFeatureSet(allSampleObj, pattern = "XIST")
allSampleObj[["percent.malat"]] <-  PercentageFeatureSet(allSampleObj, pattern = "MALAT")

allSampleObj[["CITE_Total"]] <- colSums(GetAssayData(allSampleObj, assay = "CITE"))
allSampleObj[["CITE_Features"]] <- colSums(GetAssayData(allSampleObj, assay = "CITE") > 0)

#Subset by demultiplex result
## Setting all samples with out HTO classifications (i.e. tumor samples that were not hashed) as singlet
allSampleObj$HTO_classification.global[which(is.na(allSampleObj$HTO_classification.global))] <- "Singlet"
```

```{r}
#QC Figure:

ggtable <- as.data.frame(as.matrix(table(allSampleObj$Batch)))

htoDemuxTable <- as.data.frame(as.matrix(table(allSampleObj$Batch,allSampleObj$HTO_classification.global == "Singlet"))[,"TRUE"])
ggtable$PostDemux <- htoDemuxTable[,1]

passDemux <- colnames(allSampleObj)[which(allSampleObj$HTO_classification.global == "Singlet")]
passCITE <- colnames(allSampleObj)[which(allSampleObj$CITE_Features > 50)]
passMT <- colnames(allSampleObj)[which(allSampleObj$percent.mt < 15)]
passDecont <- colnames(allSampleObj)[which(allSampleObj$DecontXContamination < 0.9)]

# passDemux <- colnames(allSampleObj)[which(allSampleObj$HTO_classification.global == "Singlet")]
# passCITE <- colnames(allSampleObj)[which(allSampleObj$CITE_Features > 20)]
# passMT <- colnames(allSampleObj)[which(allSampleObj$percent.mt < 25)]
# passDecont <- colnames(allSampleObj)[which(allSampleObj$DecontXContamination < 0.9)]

passAll <- intersect(intersect(intersect(passDemux, passCITE),passMT),passDecont)

passAllPatient <- gsub("_TL_.*","_TL", passAll)
passAllPatient <- gsub("_T_.*","_T", passAllPatient)
passAllPatient <- gsub("_L.*","_L", passAllPatient)

passQCTable <- as.data.frame(as.matrix(table(passAllPatient)))
colnames(passQCTable) <- "QC"
rownames(passQCTable) <- gsub("Patient","BUMC_LR_0",rownames(passQCTable))


#Filter to only patients 10-20
passQCTable <- passQCTable[-1,]
ggtable <- ggtable[8:25,]
ggtable <- cbind(ggtable, passQCTable)
ggtable$Sample <- c("Patient10, Tumor+LN",
                    "Patient12, LN", "Patient12, Tumor",
                    "Patient13, Tumor",
                    "Patient14, LN", "Patient14, Tumor",
                    "Patient15, LN", "Patient15, Tumor",
                    "Patient16, LN", "Patient16, Tumor",
                    "Patient17, LN", "Patient17, Tumor",
                    "Patient18, LN", "Patient18, Tumor+Normal",
                    "Patient19, LN", "Patient19, Tumor+Normal",
                    "Patient20, LN", "Patient20, Tumor+Normal")

colnames(ggtable)[1] <- "Non-droplets, Generated via CellRanger"
colnames(ggtable)[2] <- "Recovered from HTODemux, PeanutX"
colnames(ggtable)[3] <- "Post-QC"


ggtableM <- reshape2::melt(ggtable, id.vars = "Sample")
colnames(ggtableM) <- c("Sample", "Step", "Cells")

ggtableM$Sample <- factor(ggtableM$Sample, levels = unique(ggtableM$Sample))
```


```{r, fig.width = 11, fig.height = 5}
p <- ggplot(data = ggtableM, aes(x = Sample, y = Cells, fill = Step)) + geom_bar(stat="identity", color="black", position=position_dodge())+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))+ scale_fill_manual(values=c("red","green4", "darkblue"))
# pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/QC/QC_Data/Post_Demux_Decon_QC/temp.pdf", width = 11, height = 5)
p
# dev.off()
```

```{r, fig.width = 20, fig.height = 6}
allSampleObj = NormalizeData(allSampleObj, verbose = FALSE) %>%
  FindVariableFeatures(selection.method = 'vst', verbose = FALSE) %>%
  ScaleData(verbose = FALSE)
allSampleObj$Sample_HTODemux <- paste0(allSampleObj$Batch, ", ", allSampleObj$HTO_classification.global)
VlnPlot(allSampleObj, features = "ITGAX",
        assay = "RNA", group.by = "Sample_HTODemux", ) + NoLegend() + xlab("HTODemux Label Per Sample") + ggtitle("ITGAX(CD11c), RNA Expression")
```

```{r, fig.width = 15, fig.height = 5}
# allSampleObjUsed <- subset(allSampleObj, subset = Patient %in% paste0("Patient", 10:20))

allSampleObjUsed <- subset(allSampleObjUsed, subset = HTO_classification.global == "Singlet")

cd14Exprs = FetchData(allSampleObjUsed, vars = "CD14")
cd14Exprs$Threshold <- ifelse(cd14Exprs$CD14 > 0, "Above Threshold", "Below Threshold")
cd14Exprs$Sample <- gsub("_TL_.*","_TL", rownames(cd14Exprs))
cd14Exprs$Sample <- gsub("_T_.*","_T", cd14Exprs$Sample)
cd14Exprs$Sample <- gsub("_L.*","_L", cd14Exprs$Sample)

cd14PropTable <- table(cd14Exprs$Threshold, cd14Exprs$Sample) %>% prop.table(2)
cd14ThresTable <- data.frame(Sample = colnames(cd14PropTable),
                             Proportion = cd14PropTable[1,])
cd14ThresTable$SampleType <- sapply(cd14ThresTable$Sample, function(x){
    if(grepl("_TL", x)){
        return("Tumor+LN")
    }else if(grepl("_L", x)){
        return("LN")
    }else if(grepl("_T", x)){
        return("Tumor")
    }
})
cd14ThresTable$Patient <- gsub("_.*", "", cd14ThresTable$Sample)

ggplot(data = cd14ThresTable, aes(x = Patient, y = Proportion, fill = SampleType)) + geom_bar(stat="identity", color="black", position=position_dodge(preserve = "single"))+
    theme_classic() + theme(axis.text.x = element_text(angle = 45, vjust = 1,size = 12, hjust=1), axis.text.y = element_text(size = 14))+ scale_y_continuous(expand = c(0, 0))+ scale_fill_manual(values=c("darkgreen", "orange", "purple1")) + ylab("Proportion of cells with CD14 expression (> 0)")
```


