---
title: "IMC Analysis"
author: "Yusuke Koga"
output:
 html_document:
     toc: true
     toc_float: true
     number_sections: true
     theme: cosmo
     code_folding: hide
---

```{r}
# Load necessary R packages
suppressPackageStartupMessages({
    library(Seurat)
    library(dplyr)
    library(ggplot2)
    library(ggridges)
    library(gridExtra)
    library(DropletUtils)
    library(singleCellTK)
    library(celda)
    library(grDevices)
    library(pheatmap)
    library(reshape2)
    library(knitr)
    library(harmony)
    library(kableExtra)
    library(enrichR)
    library(monocle3)
    library(patchwork)
    library(SeuratWrappers)
    library(DescTools)
})

set.seed(12345)

# Define tab levels for HTML report
tab2 <- "## %s {-}
"
tab3 <- "### %s {-}
"
tab4 <- "#### %s {-}
"
tab5 <- "##### %s {-}
"
space <- "

"

```


```{r}
# Additional functions
countInteractionsPerCell <- function (object, group_by, label, colPairName){
    labelVector <- as.character(colData(object)[,label])

    if (is.factor(colData(object)[[group_by]])) {
        colData(object)[[group_by]] <- as.factor(as.character(colData(object)[[group_by]]))
    }
    cur_label <- factor(colData(object)[[label]])
    cur_table <- imcRtools:::.prepare_table(object, group_by, cur_label,
        colPairName)

    dat_temp <- dcast.data.table(cur_table, "group_by + from_label + total + from ~ to_label",
        value.var = "ct", fun.aggregate = sum, fill = 0)
    dat_temp <- melt.data.table(dat_temp, id.vars = c("group_by",
        "from_label", "from", "total"), variable.name = "to_label",
        value.name = "ct")
    total <- NULL
    dat_temp[, `:=`(ct, ct/total)]
    dat_temp <- dcast.data.table(dat_temp, "group_by + from_label ~ to_label",
        value.var = "ct", fun.aggregate = sum, fill = 0, drop = FALSE)
    dat_temp <- melt.data.table(dat_temp, id.vars = c("group_by",
        "from_label"), variable.name = "to_label", value.name = "ct")

    dcastRes <- dcast(dat_temp, formula = group_by ~ to_label, value.var = "ct", fun.aggregate=sum)
    return(dcastRes)
}
```

# Step 1. Load data, preprocessing

```{r, eval = FALSE}
spe <- read_steinbock("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Steinbock/")

# Add additional metadata
colnames(spe) <- paste0(spe$sample_id, "_", spe$ObjectNumber)

spe$image_id <- spe$sample_id

# Extract patient id and ROI id from sample name
spe$ln_id <- gsub("_.*","",spe$sample_id)
spe$patient_id <- gsub("-.*","",spe$sample_id)
spe$ROI <- str_extract(spe$sample_id, "00[1-8]")

spe$indication <- "NSCLC"

spe <- spe[,spe$area >= 20]
#Remove abnormal cell
spe <- spe[,spe$area < 500]
assay(spe, "asin") <- asinh(counts(spe)/1)

spe$Mask <- "Mask"

# Removing 13-8 as it is a metastatic LN
spe <- spe[,which(spe$ln_id != "Patient13-8")]
# Removing 15-5 due to segmentation failure 
spe <- spe[,which(spe$sample_id != "Patient15-5_ROI_001_1")]
```

# Step 2. Clustering of imaging data, 1st-pass

We will initially generate a smaller number of clusters in order to identify broader regions of cell types.

```{r, eval = FALSE}
speCelda <- spe
speCelda <- runSeuratFindHVG(speCelda, useAssay = "counts")
vstMean <- rowData(speCelda)$seurat_variableFeatures_vst_mean
vstVar <- rowData(speCelda)$seurat_variableFeatures_vst_varianceStandardized
featureName <- rownames(speCelda)

useFeature <- sapply(1:nrow(speCelda), function(x){
    if(featureName[x] %in% c("Membrane", "DNA191", "DNA193", "LAG3", "EpCAM", "CD38")){
        return(FALSE)
    }else{
        return(TRUE)
    }
})

altExp(speCelda, "featureSubset") <- speCelda[useFeature,]

speCeldaCRes <- celdaGridSearch(
  speCelda,
  useAssay = "counts",
  altExpName = "featureSubset",
  model = "celda_C",
  paramsFixed = NULL,
  maxIter = 200,
  nchains = 4,
  cores = 12,
  paramsTest = list(K = seq(3, 14)),
  bestOnly = TRUE,
  seed = 12345,
  perplexity = TRUE,
  verbose = TRUE,
  logfilePrefix = "Celda"
)
saveRDS(speCeldaCRes, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/1stPass/20241019_CeldaClustering_1stPass_NometastaticLNs_CeldaGridSearchResult_Version3.rds")

```

## Elbow plot

An elbow plot was generated for the difference between the perplexity value of a clustering result, K, and the previous clustering result, K-1(e.g., the difference between K = 5 and K = 4, etc.) in order to determine optimal number of clusters.

```{r, eval = TRUE}
speCeldaCGridSearchRes <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/1stPass/20241019_CeldaClustering_1stPass_NometastaticLNs_CeldaGridSearchResult_Version3.rds")
plotRPC(speCeldaCGridSearchRes)
```


```{r, eval = FALSE}
# K = 8 chosen as number of clusters
speCeldaCRes <- subsetCeldaList(speCeldaCGridSearchRes, params = list(K = 8))
table(altExp(speCeldaCRes)$celda_cell_cluster)

spe$CeldaClusters <- altExp(speCeldaCRes)$celda_cell_cluster
saveRDS(spe, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/1stPass/20241020_SpatialExperimentObject_NometastaticLNs_Post1stPassCeldaClustering_K8_Version3.rds")
```

# Step 2. Clustering of imaging data, 1st-pass

```{r, eval = FALSE}
spe <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/1stPass/20241020_SpatialExperimentObject_NometastaticLNs_Post1stPassCeldaClustering_K8_Version3.rds")
```

```{r, eval = FALSE}
for(clus in 1:8){
speSubset <- spe[,which(spe$CeldaClusters == clus)]
speCelda <- speSubset
speCelda <- runSeuratFindHVG(speCelda, useAssay = "counts")
vstMean <- rowData(speCelda)$seurat_variableFeatures_vst_mean
vstVar <- rowData(speCelda)$seurat_variableFeatures_vst_varianceStandardized
featureName <- rownames(speCelda)

useFeature <- sapply(1:nrow(speCelda), function(x){
    if(vstMean[x] < 5){
        return(FALSE)
    }else if(vstVar[x] < 0.5){
        return(FALSE)
    }else if(featureName[x] %in% c("Membrane", "DNA191", "DNA193", "EpCAM", "LAG3", "CD38", "CD127")){
        return(FALSE)
    }else{
        return(TRUE)
    }
})

altExp(speCelda, "featureSubset") <- speCelda[useFeature,]

speCeldaCRes <- celdaGridSearch(
  speCelda,
  useAssay = "counts",
  altExpName = "featureSubset",
  model = "celda_C",
  paramsFixed = NULL,
  maxIter = 200,
  nchains = 4,
  cores = 12,
  paramsTest = list(K = seq(2, 20)),
  bestOnly = TRUE,
  seed = 12345,
  perplexity = TRUE,
  verbose = TRUE,
  logfilePrefix = "Celda"
)
saveRDS(speCeldaCRes, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/RDS/2ndPass/20241126/20241126_CeldaClustering_2ndPass_CeldaGridSearchResult_Cluster",clus,".rds"))
}
```

## Elbow plot

```{r, results = "asis"}
cat(space)
for(x in 1:8){
    speGridSearchRes <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/RDS/2ndPass/20241126/20241126_CeldaClustering_2ndPass_CeldaGridSearchResult_Cluster",x,".rds"))
    cat(sprintf(tab3, paste0("Cluster ", x)))
    print(plotRPC(speGridSearchRes))
    cat(space)
}
```

```{r, eval = FALSE}
spe <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/1stPass/20241020_SpatialExperimentObject_NometastaticLNs_Post1stPassCeldaClustering_K8_Version3.rds")
clusterDF <- data.frame(Level2Cluster = rep("", ncol(spe)))
rownames(clusterDF) <- colnames(spe)
selectedK <- c(5, 5, 8, 5, 4, 7, 4, 5)

for(x in 1:8){
    speGridSearchRes <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/RDS/2ndPass/20241020//20241020_CeldaClustering_2ndPass_CeldaGridSearchResult_Cluster",x,"Version3.rds"))
    speCeldaCRes <- subsetCeldaList(speGridSearchRes, params = list(K = selectedK[x]))
    clusterDF[colnames(speCeldaCRes), "Level2Cluster"] <- paste0(x,"-",altExp(speCeldaCRes)$celda_cell_cluster)
}

spe$CeldaClusters2ndPass <- clusterDF$Level2Cluster

#Additional edit: 

#Combining Cluster 3:
spe$CeldaClusters2ndPass <- sapply(spe$CeldaClusters2ndPass, function(x){
    if(x %in% c("3-4", "3-5", "3-6")){
        return("3-4")
    }else if(x == "3-7"){
        return("3-5")
    }else if(x == "3-8"){
        return("3-6")
    }else{
        return(x)
    }
})

saveRDS(spe, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/RDS/2ndPass/20241126/20250719_SpatialExperimentObject_NometastaticLNs_Post2ndPassCeldaClustering_K8_Version11.rds")
```

```{r}
spe <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/RDS/2ndPass/20241126/20250716_SpatialExperimentObject_NometastaticLNs_Post2ndPassCeldaClustering_K8_Version11.rds")

spe$TumorStage <- sapply(spe$patient_id, function(x){
    if(grepl("Patient19",x)){
        return("High Stage")
    }else if(grepl("Patient15",x)){
        return("High Stage")
    }else if(grepl("Patient13",x)){
        return("High Stage")
    }else if(grepl("Patient12",x)){
        return("High Stage")
    }else{
        return("Low Stage")
    }
})

spe$N1N2 <- sapply(spe$ln_id, function(x){
  if(grepl("Tumor",x)){
      return("Tumor")
  }else if(grepl("-1",x)){
      return("N1")
  }else{
      return("N2")
  }
})
```


```{r}
genesToUse <-  c("CD19", "CD138", "CD38","FoxP3", "CD4", 
                       "CD28", "CD8a", "CD14", "CD68", "TIM3",
                       "CD163", "LAMP3", "CD141",
                       "CD1c", "CD11c", "CD45RA", "CD45RO",
                       "HLADRB", "CD86", "PDL1", 
                       "MKI67", "PD1", "CD39", "CD15", "CD127")
```

## Violin plots {.tabset}

```{r, results = "asis",  fig.width = 14, fig.height = 4}
spe$CeldaClusters2ndPass <- factor(spe$CeldaClusters2ndPass, levels = names(table(spe$CeldaClusters2ndPass)))
clusterLabel = "CeldaClusters2ndPass"
for(marker in genesToUse){
    cat(space)
    cat(sprintf(tab3, paste0(marker)))
    spe$Exprs <- assay(spe, "counts")[marker,]
    # maxCluster <- max(as.numeric(length(unique(colData(spe)[,clusterLabel]))))
    vPlotRes <- plotSCEViolinColData(inSCE = spe, coldata = "Exprs", groupBy = clusterLabel, plotOrder = levels(spe$CeldaClusters2ndPass),
                                     summary = "mean", summaryTextSize = 12,
                         xlab = paste0("Cell Populations"),
                         ylab = paste0(marker, " Expression"), baseSize = 24, title = marker)
    print(vPlotRes)
cat(space)
}
```



## Differential composition

### High Stage N1 vs Other {.tabset}

```{r, eval = FALSE}
allCellsLN <- spe

sceIMC <- SingleCellExperiment(list(counts = assay(allCellsLN)))
sceIMC$Patient <- factor(allCellsLN$patient_id)
sceIMC$LN <- factor(allCellsLN$ln_id)
sceIMC$SampleInfo <- factor(allCellsLN$sample_id)
sceIMC$N1N2 <- factor(allCellsLN$N1N2)
sceIMC$TumorStage <- factor(allCellsLN$TumorStage)
sceIMC$Cluster <- factor(allCellsLN$CeldaClusters2ndPass)
sceIMC$TumorStageN1N2 <- paste0(sceIMC$TumorStage, sceIMC$N1N2)

sceIMC$HighN1 <- factor(ifelse(sceIMC$TumorStageN1N2 == "High StageN1", 1, 0))

sccompRes =
  sceIMC |>
  sccomp_glm(
    formula_composition = ~ HighN1,
    .sample = LN,
    .cell_group = Cluster,
    bimodal_mean_variability_association = FALSE, #TRUE for CITE-seq, FALSE for IMC
    cores = 4
  )

saveRDS(sccompRes, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/ClusterLevelAssociationAnalysis/RDS/sccomp/20250715_IMCData_CeldaClusters_Version3_sccompRes_allSamples_HighN1VsOther.rds")
```

#### Tables {.tabset}

```{r}
allCellsLN <- spe
sccompRes <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/ClusterLevelAssociationAnalysis/RDS/sccomp/20250715_IMCData_CeldaClusters_Version3_sccompRes_allSamples_HighN1VsOther.rds")
sccompResSub <- sccompRes[which(sccompRes$factor == "HighN1"),]
```

##### High Stage N1 vs Other

```{r}
knitr::kable(sccompResSub[order(sccompResSub$c_FDR, decreasing = FALSE),], style = "html", row.names = TRUE) %>%
                  kable_styling(bootstrap_options = "striped") %>%
                  scroll_box(width = "100%", height = "400px")
sccompResSubTable <- sccompResSub[order(sccompResSub$c_FDR, decreasing = FALSE), c("Cluster","c_effect", "c_FDR")]
clustCount <- as.data.frame.table(table(spe$CeldaClusters2ndPass))
colnames(clustCount) <- c("Cluster", "Count")

sccompResSubTable <- merge(clustCount, sccompResSubTable)

# write.table(x = sccompResSubTable, file = "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Publication/FinalizedAnalyses/AssociationAnalysis/IMC/20250119_IMC_Cluster_Association_HigherStageN1.txt", sep = "\t", row.names = FALSE)
```

#### Volcano plots {.tabset}

##### N1/N2

```{r, fig.width = 7, fig.height = 5.5, eval = FALSE}
seuratDF <- table(allCellsLN$TumorStage, allCellsLN$CeldaClusters2ndPass) 
# seuratDF <- table(allCellsLNOnly2$stage, allCellsLNOnly2$CeldaClusters2ndPass)
seuratDF <- seuratDF %>% prop.table(1)
seuratDF <- seuratDF[,order(colnames(seuratDF))]

stageTableForFigure <- sccompResSub[!is.nan(sccompResSub$c_FDR),]
stageTableForFigure$FDR <- stageTableForFigure$c_FDR
stageTableForFigure$Estimates <- stageTableForFigure$c_effect


stageTableForFigure$Significance <- sapply(stageTableForFigure$Cluster, function(x){
    fdr = stageTableForFigure[which(stageTableForFigure$Cluster == x),"FDR"]
    coefficient = stageTableForFigure[which(stageTableForFigure$Cluster == x),"Estimates"]
    if(fdr < 0.05){
        if(coefficient < 0){
            return("Enriched, High Stage N1")
        }else{
            return("Enriched, Other")
        }
    }else{
        return("Not significant")
    }
}) 
stageTableForFigure$LogFDR <- -log(stageTableForFigure$FDR)

numCells <- as.data.frame(table(allCellsLN$CeldaClusters2ndPassNew))
colnames(numCells) <- c("Cluster", "Number of cells (in LN)")

stageTableForFigure <- merge(stageTableForFigure, numCells, by = "Cluster")

stageTableForFigure$LogFDR[which(stageTableForFigure$LogFDR > 15)] <- 15 #Adjust for plasma_0

scatterLabels <- stageTableForFigure$Cluster
scatterLabels[which(stageTableForFigure$FDR > 0.05)] <- ""

# pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20240120/AssociationAnalysis/20240410_stage_Enrichment_logit_5patients.pdf", width = 8, height = 5)
ggplot(stageTableForFigure, aes(y=LogFDR, x=-Estimates, color = Significance)) +
  geom_point(aes(size = `Number of cells (in LN)`)) +
  geom_text_repel(label=scatterLabels, show.legend=FALSE) + theme_classic()+ scale_color_manual(values=c("firebrick","orange","gray90")) + xlab("Coefficients, logit model") + xlim(c(-2, 2))+ theme(axis.text.x = element_text(size = 15), axis.text.y = element_text( size = 15), axis.title.x = element_text( size = 17), axis.title.y = element_text(size = 17), strip.text = element_text(size=15))
```


## Boxplots {.tabset}

### Stage + N1/N2 {.tabset}

```{r, results = "asis", fig.width = 5, fig.height = 5.5, message = FALSE, warning = FALSE, eval = TRUE}
spe$SampleN1N2 <- paste0(spe$ln_id, 
                              "_", spe$N1N2)
seuratDF <- table(spe$SampleN1N2, spe$CeldaClusters2ndPass) 
# seuratDF <- table(allCellsLNOnly4P$N1N2, allCellsLNOnly4P$CellTypeAnnotation) 
seuratDF <- seuratDF %>% prop.table(1)
seuratDF <- seuratDF[,order(colnames(seuratDF))]

seuratDF <- seuratDF %>% reshape2::melt()
colnames(seuratDF) <- c("Sample", "Cluster", "Value")
seuratDF$Patient <- gsub("-.*","",seuratDF$Sample)

seuratDF$Cluster <- factor(seuratDF$Cluster)
seuratDF$SampleType <- gsub(".*_","",seuratDF$Sample)

seuratDF$SampleType <- factor(seuratDF$SampleType, levels = c("N1", "N2"))

seuratDF$Stage <- sapply(seuratDF$Patient, function(x){
    if(grepl("Patient19",x)){
        return("High Stage")
    }else if(grepl("Patient15",x)){
        return("High Stage")
    }else if(grepl("Patient13",x)){
        return("High Stage")
    }else if(grepl("Patient12",x)){
        return("High Stage")
    }else{
        return("Low Stage")
    }
})

for(clust in unique(seuratDF$Cluster)){
     cat(space)
  cat(sprintf(tab4, paste0(clust)))
seuratDFSub <- seuratDF[seuratDF$Cluster == clust,]
    seuratDFSub$Value = seuratDFSub$Value * 100
    Patient = seuratDFSub$Patient
    seuratDFSub$Stage <- factor(seuratDFSub$Stage, levels = c("Low Stage", "High Stage"))
      print(ggplot(data=seuratDFSub, aes(x=Stage, y=Value)) + facet_wrap(~ SampleType, nrow = 1) +   geom_boxplot(outlier.shape = NA) + ggplot2::geom_jitter(aes(color = Patient), width = 0.1, size = 1.5)+ theme_classic()+ ylab("% within entire sample") + ggtitle(clust) + scale_y_continuous(expand = c(0, 0)) + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), axis.text.y = element_text( size = 18), axis.title.x = element_text( size = 20), axis.title.y = element_text(size = 20), strip.text = element_text(size=25), plot.title = element_text(size = 20)) +
  theme(plot.title = element_text(hjust = 0.5)) ) + scale_color_manual(values=rev(c("black","darkblue","blue","dodgerblue","seagreen","darkgreen","gold","green2","orange","red","pink"))) 
  cat(space)
}
```

# Niche generation (Kmeans) {.tabset}

```{r, eval = FALSE}
# Niche analysis, average ver

#Previous niche analysis
expansionThreshold = 50
kmeansClust = 50 #Have previously tried 40, ok

spe <- readRDS("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/RDS/2ndPass/20241126/20250719_SpatialExperimentObject_NometastaticLNs_Post2ndPassCeldaClustering_K8_Version11.rds")

#Rerun distance analysis
spe <- buildSpatialGraph(spe, img_id = "sample_id", type = "expansion", threshold = expansionThreshold)

#Rerun neighbor aggregation
spe <- aggregateNeighbors(spe, 
                          colPairName = "expansion_interaction_graph",
                          aggregate_by = "metadata", 
                          count_by = "CeldaClusters2ndPass")

#Should I be using an sum-based method rather than average? (Which is what aggregateNeighbors function above is doing)
# hist(rowSums(as.data.frame(spe$aggregatedNeighbors))) - It's all 1

#Rerun niche generation
cn_1 <- kmeans(spe$aggregatedNeighbors, centers = kmeansClust, iter.max = 10000)
spe$Niche <- as.factor(cn_1$cluster)


spe$cn_celltypes <- factor(spe$Niche)

spe$TumorStage <- sapply(spe$patient_id, function(x){
    if(grepl("Patient19",x)){
        return("High Stage")
    }else if(grepl("Patient15",x)){
        return("High Stage")
    }else if(grepl("Patient13",x)){
        return("High Stage")
    }else if(grepl("Patient12",x)){
        return("High Stage")
    }else{
        return("Low Stage")
    }
})

spe$N1N2 <- sapply(spe$ln_id, function(x){
  if(grepl("Tumor",x)){
      return("Tumor")
  }else if(grepl("-1",x)){
      return("N1")
  }else{
      return("N2")
  }
})


sceIMC <- SingleCellExperiment(list(counts = assay(spe)))
sceIMC$Patient <- factor(spe$patient_id)
sceIMC$LN <- factor(spe$ln_id)
sceIMC$SampleInfo <- factor(spe$sample_id)
sceIMC$N1N2 <- factor(spe$N1N2)
sceIMC$TumorStage <- factor(spe$TumorStage)
sceIMC$Niche <- factor(spe$cn_celltypes)
sceIMC$TumorStageN1N2 <- paste0(sceIMC$TumorStage, sceIMC$N1N2)
sceIMC$HighN1 <- factor(ifelse(sceIMC$TumorStageN1N2 == "High StageN1", 1, 0))

sccompRes =
  sceIMC |>
  sccomp_glm(
    formula_composition = ~ HighN1 + (1 | Patient),
    .sample =  LN,
    .cell_group = Niche,
    bimodal_mean_variability_association = TRUE,
    cores = 8
  )


sccompResSub <- sccompRes[which(sccompRes$factor == "HighN1"),]
sccompResSub[order(sccompResSub$c_FDR, decreasing = FALSE),]

saveRDS(spe, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/20250803_KmeansNiche",kmeansClust,"_AverageInteractionBasedNiches_Distance",expansionThreshold,".rds"))
saveRDS(sccompRes, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/20250803_KmeansNiche",kmeansClust,"_AverageInteractionBasedNiches_Distance",expansionThreshold,"_sccomp.rds"))

sceIMC$TumorStage <- factor(ifelse(sceIMC$TumorStage == "High Stage", 1, 0))
sccompRes =
  sceIMC |>
  sccomp_glm(
    formula_composition = ~ TumorStage + (1 | Patient),
    .sample =  LN,
    .cell_group = Niche,
    bimodal_mean_variability_association = TRUE,
    cores = 8
  )
sccompResSub <- sccompRes[which(sccompRes$factor == "TumorStage"),]
sccompResSub[order(sccompResSub$c_FDR, decreasing = FALSE),]
saveRDS(sccompRes, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/20250803_KmeansNiche",kmeansClust,"_AverageInteractionBasedNiches_Distance",expansionThreshold,"_sccomp_HighVsLowStage.rds"))
```

```{r}
#Previous niche analysis
expansionThreshold = 50
kmeansClust = 50 
spe <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/20250803_KmeansNiche",kmeansClust,"_AverageInteractionBasedNiches_Distance",expansionThreshold,".rds"))

sccompRes <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/IMCAnalysis/20240920/Run1/Analysis/UnsupervisedClustering/CeldaClustering/20241005_NoMets/2ndPass/20250803_KmeansNiche",kmeansClust,"_AverageInteractionBasedNiches_Distance",expansionThreshold,"_sccomp.rds"))
```

## Differential composition {.tabset}

### High Stage N1 vs Other {.tabset}

```{r}
sccompResSub <- sccompRes[which(sccompRes$factor == "HighN1"),]
sccompResSub <- as.data.frame(sccompResSub)
rownames(sccompResSub) <- paste("New", sccompResSub$Niche)
```

#### Tables {.tabset}

##### High N1 vs Other

```{r}
knitr::kable(sccompResSub[order(sccompResSub$c_FDR, decreasing = FALSE),], style = "html", row.names = TRUE) %>%
    kable_styling(bootstrap_options = "striped") %>%
    scroll_box(width = "100%", height = "400px")
```

#### Volcano plots {.tabset}

##### High N1 vs Other

```{r, fig.width = 8, fig.height = 5.5, eval = TRUE}
seuratDF <- table(spe$TumorStage, spe$cn_celltypes) 
# seuratDF <- table(speOnly2$stage, speOnly2$CeldaClusters2ndPass)
seuratDF <- seuratDF %>% prop.table(1)
seuratDF <- seuratDF[,order(colnames(seuratDF))]

sccompResSub <- sccompRes[which(sccompRes$factor == "HighN1"),]
sccompResSub <- as.data.frame(sccompResSub)
rownames(sccompResSub) <- paste("Niche", sccompResSub$Niche)

stageTableForFigure <- sccompResSub[!is.nan(sccompResSub$c_FDR),]
stageTableForFigure$FDR <- stageTableForFigure$c_FDR
stageTableForFigure$Estimates <- stageTableForFigure$c_effect
stageTableForFigure$Cluster = paste("Niche", stageTableForFigure$Niche)

stageTableForFigure$Significance <- sapply(stageTableForFigure$Cluster, function(x){
    fdr = stageTableForFigure[which(stageTableForFigure$Cluster == x),"FDR"]
    coefficient = stageTableForFigure[which(stageTableForFigure$Cluster == x),"Estimates"]
    if(fdr < 0.05){
        if(coefficient > 0){
            return("Enriched, High Stage N1")
        }else{
            return("Enriched, Other")
        }
    }else{
        return("Not significant")
    }
}) 
stageTableForFigure$LogFDR <- -log(stageTableForFigure$FDR)

numCells <- as.data.frame(table(paste0("Niche ",spe$Niche)))
colnames(numCells) <- c("Cluster", "Number of cells (in LN)")

stageTableForFigure <- merge(stageTableForFigure, numCells, by = "Cluster")

# stageTableForFigure$LogFDR[which(stageTableForFigure$LogFDR > 15)] <- 15 #Adjust for plasma_0

scatterLabels <- stageTableForFigure$Cluster
scatterLabels[which(stageTableForFigure$FDR > 0.05)] <- ""

# scatterLabelsAnnot <- sapply(scatterLabels, function(x){
#     if(x == ""){
#         return("")
#     }else{
#         clustNum = gsub("Cluster ", "", x)
#         return(paste0(celdaClusterKeyTable$Annotation[which(celdaClusterKeyTable$ID == clustNum)],
#                " (Cluster", clustNum, ")"))
#     }
# })

pdf("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20240120/AssociationAnalysis/20240410_stage_Enrichment_logit_5patients.pdf", width = 8, height = 5)
ggplot(stageTableForFigure, aes(y=LogFDR, x=Estimates, color = Significance)) +
  geom_point(aes(size = `Number of cells (in LN)`)) +
  geom_text_repel(label=scatterLabels, show.legend=FALSE) + theme_classic()+ scale_color_manual(values=c("darkorange","dodgerblue","gray90")) + xlab("Coefficients, logit model") + xlim(c(-2, 2))+ theme(axis.text.x = element_text(size = 15), axis.text.y = element_text( size = 15), axis.title.x = element_text( size = 17), axis.title.y = element_text(size = 17), strip.text = element_text(size=15)) + ylab("-log(FDR)")
```

## Boxplots {.tabset}

```{r,  results = "asis",  fig.width = 7, fig.height = 4}
spe$SampleN1N2 <- paste0(spe$ln_id, 
                              "_", spe$N1N2)
seuratDF <- table(spe$SampleN1N2, spe$cn_celltypes) 
# seuratDF <- table(speOnly4P$N1N2, speOnly4P$CellTypeAnnotation) 
seuratDF <- seuratDF %>% prop.table(1)
seuratDF <- seuratDF[,order(colnames(seuratDF))]

seuratDF <- seuratDF %>% reshape2::melt()
colnames(seuratDF) <- c("Sample", "Cluster", "Value")
seuratDF$Patient <- gsub("-.*","",seuratDF$Sample)

seuratDF$Cluster <- factor(seuratDF$Cluster)
seuratDF$SampleType <- gsub(".*_","",seuratDF$Sample)

seuratDF$SampleType <- factor(seuratDF$SampleType, levels = c("N1", "N2"))

seuratDF$Stage <- sapply(seuratDF$Patient, function(x){
    if(grepl("Patient19",x)){
        return("High Stage")
    }else if(grepl("Patient15",x)){
        return("High Stage")
    }else if(grepl("Patient13",x)){
        return("High Stage")
    }else if(grepl("Patient12",x)){
        return("High Stage")
    }else{
        return("Low Stage")
    }
})

sccompResSubSig = sccompResSub[which(sccompResSub$c_FDR < 0.05),]
sccompResSubSig = sccompResSubSig[order(sccompResSubSig$c_effect),]
sigClusts = c(sccompResSubSig$Niche, "12")

# for(clust in sigClusts){
for(clust in 1:50){
     cat(space)
  cat(sprintf(tab3, paste0(clust)))
seuratDFSub <- seuratDF[seuratDF$Cluster == clust,]
    seuratDFSub$Value = seuratDFSub$Value * 100
    Patient = seuratDFSub$Patient
    seuratDFSub$Stage <- factor(seuratDFSub$Stage, levels = c("Low Stage", "High Stage"))
      print(ggplot(data=seuratDFSub, aes(x=Stage, y=Value)) + facet_wrap(~ SampleType, nrow = 1) +   geom_boxplot(outlier.shape = NA) + ggplot2::geom_jitter(aes(color = Patient), width = 0.1, size = 1.5)+ theme_classic()+ ylab("% within entire sample") + ggtitle(paste0("Niche ",clust)) + scale_y_continuous(expand = c(0, 0)) + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), axis.text.y = element_text( size = 18), axis.title.x = element_text( size = 20), axis.title.y = element_text(size = 20), strip.text = element_text(size=25), plot.title = element_text(size = 20)) +
  theme(plot.title = element_text(hjust = 0.5))  + scale_color_manual(values=rev(c("black","darkblue","blue","dodgerblue","seagreen","darkgreen","gold","green2","orange","red","pink")))) 
  cat(space)
}
```




```{r}
sessionInfo()
```

