---
title: "20230505_SampleMerging_Filtering_2ndPassClustering_Seurat_RNAOnly"
author: "Yusuke Koga"
date: "2023-05-05"
output:
 html_document:
     toc: true
     toc_float: true
     number_sections: true
     theme: cosmo
     code_folding: hide
---


Batch correction: Not applied

Neutrophils (Cells with low RNA library size and high CD16+ ADT): NOT included

```{r}
suppressPackageStartupMessages({
    library(Seurat)
    library(dplyr)
    library(ggplot2)
    library(DropletUtils)
    library(singleCellTK)
    library(celda)
    library(grDevices)
    library(pheatmap)
    library(reshape2)
    library(knitr)
    library(harmony)
    library(kableExtra)
})


# Define tab levels
tab3 <- "### %s {-}
"
tab4 <- "#### %s {-}
"
tab5 <- "##### %s {-}
"
space <- "

"


```

```{r}
set.seed(12345)
```


```{r}
batchcor <- "no_combatseq"
neutrophil <- "with_emptydrops"
sampleType <- "BCell"
```

```{r, eval = FALSE}
allSampleObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/BCell/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_BCell.rds"))
```

# 2nd-pass clustering to identify doublets/artifacts

```{r, eval = FALSE}
allSampleObj = NormalizeData(allSampleObj, verbose = FALSE) %>%
  FindVariableFeatures(selection.method = 'vst', verbose = FALSE) %>%
  ScaleData(verbose = FALSE) %>%
  RunPCA(verbose = FALSE) 

allSampleObj<- FindNeighbors(allSampleObj, dims = 1:30, verbose = FALSE, reduction = "pca")
allSampleObj <- FindClusters(allSampleObj, resolution = 1.5, verbose = FALSE)
allSampleObj <- RunUMAP(allSampleObj, reduction = "pca", dims=1:30, verbose = FALSE)


allSampleObj[["RNACluster_BCell2ndPass"]] <- Idents(allSampleObj)
#Editing error found:
allSampleObj$Lymph_Tumor_Normal <- gsub("_.*","",allSampleObj$HashedInfo)
allSampleObj$SampleInfo[which(allSampleObj$Batch == "BUMC_LR_014_T")] <- "Patient14_Tumor"
allSampleObj$Lymph_Tumor_Normal[which(allSampleObj$Batch == "BUMC_LR_014_T")] <- "Tumor"

saveRDS(allSampleObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/",sampleType,"/20230505_2ndPass_RNAOnly_SeuratClustering_",sampleType,".rds"))
```


```{r}
allSampleObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/",sampleType,"/20230505_2ndPass_RNAOnly_SeuratClustering_",sampleType,".rds"))
```

## UMAPs {.tabset}

### Seurat Cluster

```{r}
DimPlot(allSampleObj, label = TRUE)
```

### Doublet annotation

```{r}
DimPlot(allSampleObj, group.by = "ConsensusDoublet")
```

### Ambient RNA contamination

```{r}
# DimPlot(allSampleObj, group.by = "DecontXContamination")
```

### Empty droplet

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, group.by = "EmptyDroplet")
```

### Batch

```{r}
DimPlot(allSampleObj, group.by = "Batch")
```


### Lymph/Tumor/Normal

```{r}
allSampleObj$Lymph_Tumor_Normal <- gsub("_.*","",allSampleObj$HashedInfo)
DimPlot(allSampleObj, group.by = "Lymph_Tumor_Normal")
```


## Violin Plots {.tabset}


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD19")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "MS4A1")+NoLegend()
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "MZB1")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD3D")+NoLegend()
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "GZMK")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "TCF7")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD4")
```


```{r, fig.width = 10, fig.height = 3}
dfTable <- table(allSampleObj$ConsensusDoublet, allSampleObj$RNACluster_BCell2ndPass) %>% prop.table(2)

dfTable2 <- data.frame(ConsensusDoubletRate = dfTable[1,],
                       Cluster = colnames(dfTable))
dfTable2$Cluster <- factor(dfTable2$Cluster, levels = colnames(dfTable))
dfTable2$Doublet <- sapply(dfTable2$Cluster, function(x){
    if(x %in% c(8, 19)){
        return("Doublet")
    }else{
        return("Singlet")
    }
})
dfTable2$ConsensusDoubletRate = dfTable2$ConsensusDoubletRate * 100
ggplot(data=dfTable2, aes(x=Cluster, y=ConsensusDoubletRate, fill = Doublet)) +
  geom_bar(stat="identity") + theme_classic()+scale_fill_manual(values=c("red","blue")) + ylab("Doublet %") + NoLegend()
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD8A") + NoLegend()
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "FOXP3")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "NCAM1")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "FCGR3A")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "IL7R")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "FCER1A")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD14")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "EPCAM")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "SFTPB")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "APOE")
```


```{r}
# 
# # dfExprs <- Seurat::FetchData(object = allSampleObj, assay = "CITE", c("CD45RO","CD45RA","CD3"))
# DefaultAssay(allSampleObj) <- "RNA"
# dfExprsRNA <- Seurat::FetchData(object = allSampleObj, assay = "RNA", c("CD3D","CD4","CD8A"))
# # dfExprs <- cbind(dfExprs, dfExprsRNA)
# dfExprs <- dfExprsRNA
# dfExprs$Cluster <- allSampleObj$RNACluster_BCell2ndPass
# 
# # Group by mean using dplyr
# # dfAve1 <- dfExprs %>% group_by(Cluster) %>%
# #   summarise(avg_exprs=mean(CD45RO),
# #             .groups = 'drop')
# # dfAve2 <- dfExprs %>% group_by(Cluster) %>%
# #   summarise(avg_exprs=mean(CD45RA),
# #             .groups = 'drop')
# dfAve3 <- dfExprs %>% group_by(Cluster) %>%
#   summarise(avg_exprs=mean(CD3D),
#             .groups = 'drop')
# dfAve4 <- dfExprs %>% group_by(Cluster) %>%
#   summarise(avg_exprs=mean(CD4),
#             .groups = 'drop')
# dfAve4$CD4Z <- scale(dfAve4$avg_exprs)[,1]
# dfAve5 <- dfExprs %>% group_by(Cluster) %>%
#   summarise(avg_exprs=mean(CD8A),
#             .groups = 'drop')
# dfAve4$CD8Z <- scale(dfAve5$avg_exprs)[,1]
# 
# TcellLabel <- sapply(1:nrow(dfAve4), function(x){
#     if(dfAve4[x,"CD4Z"] > 0){
#         return("CD4")
#     }else if(dfAve4[x,"CD8Z"] > 0){
#         return("CD8")
#     }else{
#         return("other")
#     }
# })
# 
# plot(dfAve4$CD4Z, dfAve4$CD8Z, pch = 3)
# text(dfAve4$CD4Z, dfAve4$CD8Z, labels = dfAve4$Cluster)
# 
# ggDFAve <- cbind(dfAve1$avg_exprs[which(dfAve3$avg_exprs > 0.4)], dfAve2$avg_exprs[which(dfAve3$avg_exprs > 0.4)])
# ggDFAve <- as.data.frame(ggDFAve)
# ggDFAve$Type <- TcellLabel[which(dfAve3$avg_exprs > 0.4)]
# rownames(ggDFAve) <- paste("Cluster",dfAve1$Cluster[which(dfAve3$avg_exprs > 0.4)])
# colnames(ggDFAve) <- c("CD45RO", "CD45RA","Type")
```


### Gene set enrichment results {.tabset}

WARNING: Gene set enrichment results generated from differential expression analysis results should be analyzed with caution, due to the unreliability of tools. Avoid overinterpretation.

```{r, results = "asis", eval = FALSE, message=FALSE}
# allMarkersRNA <- FindAllMarkers(allSampleObj)
# saveRDS(allMarkersRNA, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/",sampleType,"/20230505_Seurat_2ndPass_Multimodal_FindMarkers_RNA_",sampleType,".rds"))
allMarkersRNA <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/",sampleType,"/20230505_Seurat_3rdPass_Multimodal_FindMarkers_RNA_",sampleType,".rds"))

findMarkerRes <- allMarkersRNA
dbs <- c("PanglaoDB_Augmented_2021",  "Azimuth_Cell_Types_2021", "MSigDB_Hallmark_2020", "Reactome_2022")

for(clust in unique(allMarkersRNA$cluster)) {
    # aveExpGene <- rowMeans(GetAssayData(allSampleObj, assay = "RNA")[,which(allSampleObj$ADTCluster == clust)])
    # sdExpGene <- apply(GetAssayData(allSampleObj, assay = "RNA")[,which(allSampleObj$ADTCluster == clust)], 1, sd)
    findMarkerResSub <- findMarkerRes %>% dplyr::filter(cluster == clust)
    findMarkerResSub <- findMarkerResSub[order(findMarkerResSub$avg_log2FC , decreasing = T),]
    findMarkerResSub <- findMarkerResSub[which(findMarkerResSub$p_val_adj < 0.05),]
    findMarkerResSub <- findMarkerResSub[which(findMarkerResSub$avg_log2FC > 0.25),]
    if(nrow(findMarkerResSub) > 0){
        cat(sprintf(tab4, paste0("Cluster ", clust, " {.tabset}\n")))
        enriched <- enrichr(findMarkerResSub$gene, dbs)
        cat(space)
        
        cat(sprintf(tab5, "Celltype enrichment, PanglaoDB 2021"))
        print(knitr::kable(enriched$PanglaoDB_Augmented_2021, style = "html", row.names = FALSE) %>%
                  kable_styling(bootstrap_options = "striped") %>%
                  scroll_box(width = "100%", height = "800px"))
        cat(space)
        
        cat(sprintf(tab5, "Celltype enrichment, Azimuth 2021"))
        print(knitr::kable(enriched$Azimuth_Cell_Types_2021, style = "html", row.names = FALSE) %>%
                  kable_styling(bootstrap_options = "striped") %>%
                  scroll_box(width = "100%", height = "800px"))
        cat(space)
        
        cat(sprintf(tab5, "Pathway enrichment, MSigDB Hallmarks 2020"))
        print(knitr::kable(enriched$MSigDB_Hallmark_2020, style = "html", row.names = FALSE) %>%
                  kable_styling(bootstrap_options = "striped") %>%
                  scroll_box(width = "100%", height = "800px"))
        cat(space)
        
        cat(sprintf(tab5, "Pathway enrichment, Reactome 2022"))
        print(knitr::kable(enriched$Reactome_2022, style = "html", row.names = FALSE) %>%
                  kable_styling(bootstrap_options = "striped") %>%
                  scroll_box(width = "100%", height = "800px"))
        cat(space)
        
        
  cat(space)
    }
    
    # if(clust == 0){
    #     dfTopGenes = data.frame(Gene = head(findMarkerResSub$gene,10),
    #                             Cluster = rep(clust,10))
    # }else{
    #     dfTopGenesSub = data.frame(Gene = head(findMarkerResSub$gene,10),
    #                             Cluster = rep(clust,10))
    #     dfTopGenes = rbind(dfTopGenes, dfTopGenesSub)
    # }
}


```



# Subset data

Will subset cluster 8, 19, 20 due to likelihood of being T lymphocyte. Given expression of CD3D, CD4, CD56 expression, expression of MS4A1/CD19, this population will be removed.

```{r}
bCellClusters = levels(allSampleObj$RNACluster_BCell2ndPass)
bCellClusters = bCellClusters[-which(bCellClusters %in% c(8, 19, 20))]
allSampleObj <- subset(allSampleObj, RNACluster_BCell2ndPass %in% bCellClusters)
dim(allSampleObj)
```

```{r}
saveRDS(allSampleObj, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/BCell/20230505_3rdPass_RNAOnly_SeuratClustering_BCell_PostFilter.rds")
```


