---
title: "20230505_SampleMerging_Filtering_2ndPassClustering_Seurat_RNAOnly"
author: "Yusuke Koga"
date: "2023-05-05"
output:
 html_document:
     toc: true
     toc_float: true
     number_sections: true
     theme: cosmo
     code_folding: hide
---


Batch correction: Not applied

Neutrophils (Cells with low RNA library size and high CD16+ ADT): NOT included

```{r}
suppressPackageStartupMessages({
    library(Seurat)
    library(dplyr)
    library(ggplot2)
    library(DropletUtils)
    library(singleCellTK)
    library(celda)
    library(grDevices)
    library(pheatmap)
    library(reshape2)
    library(knitr)
    library(harmony)
    library(kableExtra)
})


# Define tab levels
tab3 <- "### %s {-}
"
tab4 <- "#### %s {-}
"
tab5 <- "##### %s {-}
"
space <- "

"


```

```{r}
set.seed(12345)
```


```{r}
batchcor <- "no_combatseq"
sampleType <- "TNK"
```

```{r}
allSampleObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/TNK/20230505_", batchcor,"_allSampleObj_PostSeurat_RNAClustering_TNK.rds"))
```

# 2nd-pass clustering to identify doublets/artifacts

```{r, eval = TRUE}
allSampleObj = NormalizeData(allSampleObj, verbose = FALSE) %>%
  FindVariableFeatures(selection.method = 'vst', verbose = FALSE) %>%
  ScaleData(verbose = FALSE) %>%
  RunPCA(verbose = FALSE) 

allSampleObj<- FindNeighbors(allSampleObj, dims = 1:30, verbose = FALSE, reduction = "pca")
allSampleObj <- FindClusters(allSampleObj, resolution = 1.5, verbose = FALSE)
allSampleObj <- RunUMAP(allSampleObj, reduction = "pca", dims=1:30, verbose = FALSE)


allSampleObj[["RNACluster_TNK2ndPass"]] <- Idents(allSampleObj)
#Editing error found:
allSampleObj$Lymph_Tumor_Normal <- gsub("_.*","",allSampleObj$HashedInfo)
allSampleObj$SampleInfo[which(allSampleObj$Batch == "BUMC_LR_014_T")] <- "Patient14_Tumor"
allSampleObj$Lymph_Tumor_Normal[which(allSampleObj$Batch == "BUMC_LR_014_T")] <- "Tumor"
saveRDS(allSampleObj, paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/",sampleType,"/20230505_2ndPass_RNAOnly_SeuratClustering_",sampleType,".rds"))
```


```{r}
allSampleObj <- readRDS(paste0("/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/2ndPass/",sampleType,"/20230505_2ndPass_RNAOnly_SeuratClustering_",sampleType,".rds"))
```

## UMAPs {.tabset}

### Seurat Cluster

```{r}
DimPlot(allSampleObj, label = TRUE)
```

### Doublet annotation

```{r}
DimPlot(allSampleObj, group.by = "ConsensusDoublet")
```

### Ambient RNA contamination

```{r}
# DimPlot(allSampleObj, group.by = "DecontXContamination")
```


### Batch

```{r}
DimPlot(allSampleObj, group.by = "Batch")
```


### Empty droplet

```{r, fig.width = 10, fig.height = 8, eval = TRUE}
DimPlot(allSampleObj, group.by = "EmptyDroplet")
```

### Lymph/Tumor/Normal

```{r}
allSampleObj$Lymph_Tumor_Normal <- gsub("_.*","",allSampleObj$HashedInfo)
DimPlot(allSampleObj, group.by = "Lymph_Tumor_Normal")
```


## Violin Plots {.tabset}

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD3D")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD4")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD8A")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "FOXP3")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "NCAM1")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "FCGR3A")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "IL7R")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "TRGV9")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "TRDV2")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "FCER1A")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD14")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "EPCAM")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "APOE")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "CD19")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "MS4A1")
```


```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "MZB1")
```

```{r, fig.width = 10, fig.height = 3}
VlnPlot(allSampleObj, "MKI67")
```

```{r}
# 
# # dfExprs <- Seurat::FetchData(object = allSampleObj, assay = "CITE", c("CD45RO","CD45RA","CD3"))
# DefaultAssay(allSampleObj) <- "RNA"
# dfExprsRNA <- Seurat::FetchData(object = allSampleObj, assay = "RNA", c("CD3D","CD4","CD8A"))
# # dfExprs <- cbind(dfExprs, dfExprsRNA)
# dfExprs <- dfExprsRNA
# dfExprs$Cluster <- allSampleObj$RNACluster_TNK2ndPass
# 
# # Group by mean using dplyr
# # dfAve1 <- dfExprs %>% group_by(Cluster) %>%
# #   summarise(avg_exprs=mean(CD45RO),
# #             .groups = 'drop')
# # dfAve2 <- dfExprs %>% group_by(Cluster) %>%
# #   summarise(avg_exprs=mean(CD45RA),
# #             .groups = 'drop')
# dfAve3 <- dfExprs %>% group_by(Cluster) %>%
#   summarise(avg_exprs=mean(CD3D),
#             .groups = 'drop')
# dfAve4 <- dfExprs %>% group_by(Cluster) %>%
#   summarise(avg_exprs=mean(CD4),
#             .groups = 'drop')
# dfAve4$CD4Z <- scale(dfAve4$avg_exprs)[,1]
# dfAve5 <- dfExprs %>% group_by(Cluster) %>%
#   summarise(avg_exprs=mean(CD8A),
#             .groups = 'drop')
# dfAve4$CD8Z <- scale(dfAve5$avg_exprs)[,1]
# 
# TcellLabel <- sapply(1:nrow(dfAve4), function(x){
#     if(dfAve4[x,"CD4Z"] > 0){
#         return("CD4")
#     }else if(dfAve4[x,"CD8Z"] > 0){
#         return("CD8")
#     }else{
#         return("other")
#     }
# })
# 
# plot(dfAve4$CD4Z, dfAve4$CD8Z, pch = 3)
# text(dfAve4$CD4Z, dfAve4$CD8Z, labels = dfAve4$Cluster)
# 
# ggDFAve <- cbind(dfAve1$avg_exprs[which(dfAve3$avg_exprs > 0.4)], dfAve2$avg_exprs[which(dfAve3$avg_exprs > 0.4)])
# ggDFAve <- as.data.frame(ggDFAve)
# ggDFAve$Type <- TcellLabel[which(dfAve3$avg_exprs > 0.4)]
# rownames(ggDFAve) <- paste("Cluster",dfAve1$Cluster[which(dfAve3$avg_exprs > 0.4)])
# colnames(ggDFAve) <- c("CD45RO", "CD45RA","Type")
```

# Subset data

Will subset cluster 34 due to likelihood of being B lymphocyte. Given the lack of CD3D, CD4, CD56 expression, expression of MS4A1/CD19, this population will be moved to the B cell population. (This population likely clustered here because of MKI67 expression)

Subset cluster 29 due to likelihood of myeloid population. Given the lack of CD3D, CD4, CD56 expression, expression of CSF3R, DUSP1, overall low expression, previously an empty droplet. 

```{r}
allSampleObjSub <- subset(allSampleObj, RNACluster_TNK2ndPass != 34)
allSampleObjSub <- subset(allSampleObjSub, RNACluster_TNK2ndPass != 29)
bCellSub <- subset(allSampleObj, RNACluster_TNK2ndPass == 34)
```

```{r}
saveRDS(allSampleObjSub, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/TNK/20230505_3rdPass_RNAOnly_SeuratClustering_TNK_PostFilter.rds")

saveRDS(bCellSub, "/restricted/projectnb/camplab/projects/20220504_Suzuki_LN/Analysis/Clustering/20230505/3rdPass/BCell/20230505_3rdPass_RNAOnly_SeuratClustering_bCell_SubFromTNK.rds")
```


